\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage{hyperref}
%\usepackage{href}


\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

%\usepackage[margin=0.0in]{geometry}
\usepackage{geometry}
 \geometry{
% a4paper,
 total={170mm,257mm},
 left=1in,
 top=20mm,
 }

% \leftmargin=0.25in
% \oddsidemargin=0.25in
% \textwidth=6.0in
% \topmargin=-0.25in
% \textheight=9.25in

\raggedright

\pagenumbering{gobble}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

\newcommand{\tab}{\hspace*{2em}}

\newcommand{\bul}{$\bullet$ \hspace*{0em}}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{changemargin}{-0.5in}{-0.5in}
\centering{{\Huge \scshape {\textbf{Brando Miranda}}}}\\ 
\vspace{10 pt}
\centering{
{ 
\href{https://scholar.google.com/citations?user=_NQJoBkAAAAJ&hl=en}{Google Scholar};
\href{https://brando90.github.io/brandomiranda/}{Website};
\href{https://profiles.stanford.edu/brando-miranda}{Stanford Profile};
\href{https://cbmm.mit.edu/about/people/miranda}{MIT Website}
}
\\  
\vspace{-30 pt}

\textbf{brando9@stanford.edu}
\hfill Gates Bldg., 353 Jane Stanford Way \\
Stanford, CA, 94305. \hfill 
\vspace{7 pt}
} % Add this closing brace here
\end{changemargin}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{Ph.D. in Computer Science} \hfill \emph{2022-2026 (expected)}\\
	\emph{Stanford University} \hfill \text{GPA: 4.045/4.0}\\
	Advisor: Prof. Sanmi Koyejo, Stanford Trustworthy AI Research (STAIR) group\\
	Fellowships: Stanford School of Engineering Fellowship, EDGE Scholar\\
	\textbf{Master of Engineering in Electrical Engineering and Computer Science} \hfill \emph{2014-2016}\\
	\emph{Massachusetts Institute of Technology} \hfill \text{GPA: 4.8/5.0}\\
	Advisor: Prof. Tomaso Poggio, Center for Brains, Minds and Machines (CBMM)\\
	\textbf{Bachelor of Science, Computer Science and Engineering} \hfill \emph{2010-2014} \\
	\emph{Massachusetts Institute of Technology} \hfill \text{minor in Mathematics \& Music}\\
\end{body}

%\medskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Coursework}

\begin{body}
	\vspace{14pt}
	\begin{tabbing}
	\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm} \kill
	\bul Statistical Learning Theory \> \> \> \> \> \bul Intro to Machine Learning \> \> \> \> \> \> \bul Algorithmic Aspects of Machine Learning  \\
	\bul Artificial Intelligence \> \> \> \> \> \bul Probability \& Random Variables \> \> \> \> \> \> \bul Algorithms for Inference (PGMs) \\
	\bul Linear Algebra \> \> \> \> \> \bul Computability \& Complexity \> \> \> \> \> \> \bul Design \& Analysis of Algorithms \\
	\bul Distributed Systems \> \> \> \> \> \bul Differential Equations \> \> \> \> \> \> \bul Online Methods in Machine Learning \\
    \bul Computer System Security \> \> \> \> \> \bul Computer System Engineering \> \> \> \> \> \> \bul Programming Language Semantics  \\
    \bul Learning to Learn \> \> \> \> \> \bul Reinforcement Learning \& MDPs \> \> \> \> \> \>  \bul Formal Software Development Methods \\
    \bul Multi-variable Calculus \> \> \> \> \> \bul Mathematical Logic \> \> \> \> \> \>  \bul Advances in Foundation Models \\
	\end{tabbing}
	\end{body}
%\medskip
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Experience
\header{Research Experience}

\begin{body}
	\vspace{16pt}
 
 	\textbf{Stanford University} - Stanford, CA \hfill \emph{September 2022 - 2026 (expected)}\\
	\emph{Ph.D. Student in Computer Science}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item Machine Learning PhD student with professor Sanmi Koyejo conducting research on data-centric machine learning for Frontier Models, formal reasoning and verification, and scaling laws for LLMs.
		\item Published award-winning work challenging prevailing notions of ``emergent abilities'' in large language models (NeurIPS Outstanding Paper Award 2023).
		\item Leading development of VeriBench and Putnam-AXIOM benchmarks for evaluating AI mathematical reasoning (both accepted at ICML 2025).
		\item Research mentor for undergraduate and master's students focused on data quality for Foundation Models.
	\end{itemize}
	\vspace{5 pt}

	\textbf{Morph Labs} - Remote \hfill \emph{2023}\\
	\emph{Machine Learning Research Scientist Consultant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Made key contributions to Morph Prover v0-7B, the first frontier model for the Lean 4 formal verification programming language.
		\item Helped launch Moogle.ai, the first search engine for verified code in Lean.
	\end{itemize}
	\vspace{5 pt}

	\textbf{Wise Agents} - Stanford Spin-out \hfill \emph{2023}\\
	\emph{AI Research Consultant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Deployed AI agent-based systems to transform sales performance.
		\item Company featured in Forbes Mexico.
	\end{itemize}
	\vspace{5 pt}

	\textbf{IBM - ML Research Internship} - Yorktown Heights, NY \hfill \emph{May 2022 - August 2022}\\
	\emph{Graduate Research Intern}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item PhD research intern studying the ability of Transformer models to predict mathematical formal proofs using the program representation in the theorem proving language of Coq.
	\end{itemize}

	\textbf{University of Illinois Urbana-Champaign} - Urbana-Champaign, IL \hfill \emph{September 2018 - 2021}\\
	\emph{Graduate Student}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item PhD student with professor Sanmi Koyejo working on the foundations of meta-learning and cognitively inspired deep learning methods for program synthesis, theorem proving and reasoning.
	\end{itemize}
	\vspace{5 pt}
	
	\textbf{IBM - ML Research Internship} - Yorktown Heights, NY \hfill \emph{May 2021 - August 2021}\\
	\emph{Graduate Research Intern}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item PhD Research Intern studying the optimization and architectural inductive biases of Transformer models for the task of type inference of programs. 
	\end{itemize}
	\vspace{5 pt}

	\textbf{MIT CBMM (Center for Brain Minds \& Machines)} - Cambridge, MA \hfill \emph{June 2015 - September 2018}\\
	\emph{Research Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
        \item Research assistant with professor Tomaso Poggio working on Deep Learning Theory
        \item Graduate research assistant, thesis topic; Training methods for Deep Gaussian Networks and function approximation for compositional hierarchical functions
        \item My website at CBMM: \href{https://cbmm.mit.edu/about/people/miranda}{https://cbmm.mit.edu/about/people/miranda}
	\end{itemize}
	\vspace{5 pt}
    
	\textbf{MIT CBMM (Center for Brain Minds \& Machines), UIUC \& Stanford} \hfill \emph{June 2016 - present}\\
	\emph{Research Mentor}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
        \item Stanford: Research mentor with an Undergraduate and two master students on studying data quality for Foundation Models.
        \item UIUC: Research mentor for the REU programs
        \item MIT CBMM: Research leader mentoring undergraduates with the Engineering of Intelligence Team \href{https://cbmm.mit.edu/eit/people}{(EIT)}
	\end{itemize}
	\vspace{5 pt}
    
 %        \textbf{MIT (Undergraduate Research Opportunity Program)} - Cambridge, MA \hfill \emph{June 2012 - August 2012}\\
	% \emph{Undergraduate Research Assistant}\\
	% \vspace*{-3pt}
	% \begin{itemize} \itemsep -2pt
	% 	\item Project: Crowd-Sourcing the Design of Drug-Delivery Vehicles for Cancer Treatment
 %        \item Developed user interface (UI) that enables the general population to design drug delivery vehicles for cancer treatment
 %        \item Built the communication network allowing reliable interaction amongst the user interface, database and back-end of the project
 %        \item Presented and explained the project to the research lab.
	% \end{itemize}
    
\end{body}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\header{Publications}
\begin{body}
    \vspace{4pt} % DONT REMOVE THIS

    \vspace{8pt}
    \emph{Google Scholar metrics: 2,948+ citations | h-index: 17 | i10-index: 22}

    \vspace{12pt}
    \textbf{\large 2025}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://arxiv.org/pdf/2406.04391}
    {R. Schaeffer, H. Schoelkopf, B. Miranda, G. Mukobi, V. Madan, A. Ibrahim, H. Bradley, S. Biderman, S. Koyejo,
    Why Has Predicting Downstream Capabilities of Frontier AI Models with Scale Remained Elusive?}
    \\
    (\textbf{ICML 2025} \& \textbf{ICML TiFA Workshop Outstanding Paper Award 2024})

    \vspace{10pt}
    {A. Gulati, B. Miranda, E. Chen, E. Xia, K. Fronsdal, B. de Moraes Dumont, S. Koyejo,
    Putnam-AXIOM: A Functional \& Static Benchmark for Measuring Higher Level Mathematical Reasoning in LLMs.}
    \\
    (\textbf{ICML 2025} \& NeurIPS MATH-AI Workshop 2024)

    \vspace{10pt}
    {B. Miranda, Z. Zhou, A. Nie, E. Obbad, L. Aniva, K. Fronsdal, W. Kirk, D. Soylu, et al.,
    VeriBench: End-to-End Formal Verification Benchmark for AI Code Generation in Lean 4.}
    \\
    (\textbf{2nd AI for Math Workshop @ ICML 2025})

    \vspace{10pt}
    {Z. Zhou, X. Lu, C. Cao, B. Miranda, T. Liu, B. Han, S. Koyejo,
    CoDaPO: Confidence and Difficulty-Adaptive Policy Optimization for Post-Training Language Models.}
    \\
    (\textbf{2nd AI for Math Workshop @ ICML 2025})

    \vspace{10pt}
    \href{https://link.springer.com/chapter/10.1007/978-3-031-90643-5_6}
    {L. Aniva, C. Sun, B. Miranda, C. Barrett, S. Koyejo,
    Pantograph: A machine-to-machine interaction interface for advanced theorem proving, high level reasoning, and data extraction in Lean 4.}
    \\
    (\textbf{TACAS 2025} - International Conference on Tools and Algorithms for the Construction and Analysis of Systems)

    \vspace{10pt}
    {R. Schaeffer, B. Miranda, J. Kazdan, K. Liu, A. M. Ahmed, N. Mireshghallah, et al.,
    Causally Quantifying the Effect of Test Set Contamination on Generative Benchmarks.}
    \\
    (NeurIPS 2025 Workshop on Evaluating the Evolving LLM Lifecycle)

    \vspace{10pt}
    {R. Schaeffer, J. Kazdan, Y. Denisov-Blanch, B. Miranda, M. Gerstgrasser, et al.,
    Position: Machine Learning Conferences Should Establish a `Refutations and Critiques' Track.}
    \\
    (Preprint 2025)

    \vspace{12pt}
    \textbf{\large 2024}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://openreview.net/forum?id=wvFnqVVUhN}
    {R. Schaeffer, D. Valentine, L. Bailey, J. Chua, et al., B. Miranda, et al., S. Koyejo, E. Perez,
    Failures to Find Transferable Image Jailbreaks Between Vision-Language Models.}
    \\
    (\textbf{ICLR 2024} \& NeurIPS Red Teaming GenAI Workshop 2024)

    \vspace{10pt}
    {R. Schaeffer, M. Khona, S. Chandra, M. Ostrow, B. Miranda, S. Koyejo,
    Does Maximizing Neural Regression Scores Teach Us About The Brain?}
    \\
    (UniReps Workshop 2nd Edition, NeurIPS 2024)

    \vspace{10pt}
    {K. Chawla, A. Sahai, M. DePavia, S. Sundar, B. Miranda,
    Quantifying the Importance of Data Alignment in Downstream Model Performance.}
    \\
    (ICLR 2024 Workshop on Data-centric Machine Learning Research)

    \vspace{10pt}
    {A. Gulati, D. Ladsaria, S. Mishra, J. Sidhu, B. Miranda,
    An Evaluation Benchmark for Autoformalization in Lean4.}
    \\
    (The Second Tiny Papers Track at ICLR 2024)

    \vspace{12pt}
    \textbf{\large 2023}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://arxiv.org/abs/2304.15004}
    {R. Schaeffer, B. Miranda, S. Koyejo,
    Are Emergent Abilities of Language Models a Mirage?}
    \\
    (\textbf{NeurIPS Outstanding Paper Award \& Oral 2023}, Stanford IEEE Invited Talk 2023)
    \\
    Featured in: New York Times, Quanta Magazine, Forbes, Stanford HAI.
    Cited in the 2024 Economic Report of the President (White House).

    \vspace{10pt}
    {B. Miranda (ML Research Scientist Consultant) \& Morph Labs Team,
    Morph Prover v0 7b: The 1st Frontier Model for the Lean 4 Formal Verification Programming Language.}
    \\
    \href{https://morph.so/blog/the-personal-ai-proof-engineer/}{[Blog]}
    \href{https://huggingface.co/morph-labs/morph-prover-v0-7b}{[Hugging Face Model Card]}

    \vspace{10pt}
    \href{https://arxiv.org/abs/2306.13840}
    {A. Lee*, B. Miranda*, P. Yu, S. Koyejo,
    Beyond Scale: the Diversity Coefficient as a Data Quality Metric Demonstrates LLMs are Pre-trained on Formally Diverse Data.}
    \\
    (ICML Data-Centric ML Workshop \& ICML Deployable Generative AI Workshop 2023) (*equal contribution)

    \vspace{10pt}
    \href{https://arxiv.org/abs/2306.13841}
    {B. Miranda, P. Yu, S. Goyal, Y. Wang, S. Koyejo,
    Is Pre-training Truly Better Than Meta-Learning?}
    \\
    (Preprint 2023)

    \vspace{10pt}
    {B. Miranda, A. Shinnar, V. Pestun, B. Trager,
    Transformer Models for Type Inference in the Simply Typed Lambda Calculus: A Case Study in Deep Learning for Code.}
    \\
    (Preprint 2023)

    \vspace{12pt}
    \textbf{\large 2022}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://arxiv.org/abs/2208.01545}
    {B. Miranda, P. Yu, Y. Wang, S. Koyejo,
    The Curse of Zero Task Diversity: the Failure of Transfer Learning to Outperform MAML and their Empirical Equivalence.}
    \\
    (NeurIPS Contributed Talk - Meta-learning Workshop 2022)

    \vspace{12pt}
    \textbf{\large 2021}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://arxiv.org/abs/2112.13137}
    {B. Miranda, Y. Wang, S. Koyejo,
    Does MAML Only Work via Feature Re-use? A Data Set Centric Perspective.}
    \\
    (Preprint 2021)

    \vspace{12pt}
    \textbf{\large 2020}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://www.ideals.illinois.edu/handle/2142/109139}
    {B. Miranda,
    An Empirical Study of Meta-Learning: a step towards rigorously understanding meta-learning algorithms.}
    \\
    (Preprint 2020)

    \vspace{12pt}
    \textbf{\large 2019}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://drive.google.com/file/d/1G2IVmbENphwB3lxROEpCHQjsClKqRtKP/view}
    {T. Poggio, A. Banburski, Q. Liao, B. Miranda, L. Rosasco, J. Hidary,
    Weight and Batch Normalization implement Classical Generalization Bounds.}
    \\
    (ICML Workshop 2019)

    \vspace{10pt}
    \href{https://arxiv.org/abs/1903.04991}
    {A. Banburski, Q. Liao, B. Miranda, L. Rosasco, B. Liang, J. Hidary, T. Poggio,
    Theory III: Dynamics and Generalization in Deep Networks.}
    \\
    (Preprint 2019)

    \vspace{12pt}
    \textbf{\large 2018}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://arxiv.org/abs/1807.09659}
    {Q. Liao, B. Miranda, A. Banburski, J. Hidary, T. Poggio,
    A Surprising Linear Relationship Predicts Test Performance in Deep Networks.}
    \\
    (Preprint 2018)

    \vspace{10pt}
    \href{https://arxiv.org/abs/1801.02254}
    {C. Zhang, Q. Liao, A. Rakhlin, B. Miranda, N. Golowich, T. Poggio,
    Theory of Deep Learning IIb: Optimization Properties of SGD.}
    \\
    (Preprint 2018)

    \vspace{10pt}
    \href{https://arxiv.org/abs/1806.11379}
    {T. Poggio, Q. Liao, B. Miranda, A. Banburski, X. Boix, J. Hidary,
    Theory IIIb: Generalization in Deep Networks.}
    \\
    (Preprint 2018)

    \vspace{10pt}
    \href{https://www.osapublishing.org/abstract.cfm?uri=CLEO_SI-2018-SF1A.1}
    {D. Kita, B. Miranda, H. Lin, J. Michon, D. Favela, J. Hu,
    High-resolution on-chip digital Fourier transform spectroscopy.}
    \\
    (CLEO: Science and Innovations 2018)

    \vspace{10pt}
    \href{https://www.nature.com/articles/s41467-018-06773-2}
    {D. Kita, B. Miranda, D. Favela, D. Bono, J. Michon, H. Lin, T. Gu, J. Hu,
    High-performance and scalable on-chip digital Fourier transform spectroscopy.}
    \\
    (\textbf{Nature Communications} 9 (1), 4405. 2018)

    \vspace{12pt}
    \textbf{\large 2017}
    \vspace{4pt}

    \vspace{10pt}
    \href{https://arxiv.org/abs/1801.00173}
    {T. Poggio, K. Kawaguchi, Q. Liao, B. Miranda, L. Rosasco, X. Boix, J. Hidary, M. Mhaskar,
    Theory of Deep Learning III: explaining the non-overfitting puzzle.}
    \\
    (Preprint 2017)

    \vspace{10pt}
    \href{https://link.springer.com/article/10.1007/s11633-017-1054-2}
    {T. Poggio, H. Mhaskar, L. Rosasco, B. Miranda, Q. Liao,
    Why and when can deep-but not shallow-networks avoid the curse of dimensionality: A review.}
    \\
    (\textbf{International Journal of Automation and Computing}, pp. 1-17, 2017. \textbf{Most Cited Paper Certificate.})

    \vspace{4pt}
\end{body}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards & Honors

\header{Awards \& Honors}
\begin{body}
\vspace{16pt}
\begin{itemize} \itemsep -2pt
    \item ICML Outstanding Paper TiFA Workshop Award (July 2024)
    \item NeurIPS Outstanding Main Track Paper Award, (December 11, 2023) (top 0.4\% and only 2 papers selected)
    \item EDGE Scholar, Stanford University (September 2022)
    \item Stanford School of Engineering fellowship, Stanford University (September 2022)
    \item Honorable Mention, Ford Foundation Fellowship (2021)
    \item Best research project award for the UIUC graduate course CS 598 ``Learning to Learn" by professor Y. Wang (December 2020).
    \item HSF (Hispanic Scholarship Fund) Scholar (2020)
    \item Honorable Mention, Ford Foundation Fellowship (2020)
    \item Most Cited Paper Certificate, International Journal of Automation \& Computing (IJAC) (December 2019)
    \item Computer Science Excellence Saburo Muroga Endowed Fellow, (2019-2020)
	\item Sloan Scholar, Alfred P. Sloan Foundation’s Minority Ph.D. (MPHD) Program, awarded in (2018-2019)
	\item Grainger Engineering SURGE Fellowship, awarded in (2018-2019)
	\item Chopper Trading, LLC, Best Strategy Report award, MIT Battle Code AI competition (2013)
	\item MIT Mitchell B. Kaufman Memorial Scholarship (2012-2013, 2013-2014)
	\item MIT Eugene and Margaret (HM) McDermott Scholarship (2012-2013, 2013-2014)
 	\item Greengates Scholarship (30\% 2007, 50\% 2008, 100\% 2009, 100\% 2010)
	\item High Achievement Prize Award, Greengates School (2007, 2008, 2009, 2010) -- similar to Valedictorian
        \item Achievement Prize award, Greengates School (2006)
	\item Best all round student award, Greengates School (2010)
	\item Certificate for Progress award, Greengates School (2005)
\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Media Coverage

\header{Media Coverage}
\begin{body}
\vspace{16pt}
\begin{itemize} \itemsep -2pt
    \item \textbf{White House Economic Report of the President (2024)}: Our work on emergent abilities was cited in the official economic report to the President
    \item \textbf{The New York Times (2023)}: ``Silicon Valley Confronts the Idea That the `Singularity' Is Here''
    \item \textbf{Quanta Magazine (2024)}: ``How Quickly Do Large Language Models Learn Unexpected Skills?''
    \item \textbf{Forbes (2023)}: ``AI `Emergent Abilities' Are A Mirage, Says AI Researcher''
    \item \textbf{Andrew Ng (2024)}: Endorsed our paper as evidence that AGI development will be smooth and predictable
    \item \textbf{Additional coverage}: Stanford HAI, Y Combinator News, Vice, Medium, HackerNews, NeurIPS blog
\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Poster Presentations

\header{Presentations and Posters}

\begin{body}

% \subheader{Posters}

% 1) MIT Quest for Intelligence launch
% 2) Center for Brains, Minds and Machines annual National Science Foundation meeting
% 3) CBMM External Advisory Committee Meeting.
% 4) guest lecture 9.520 neural nets

% There was an ICML 2019 poster at a workshop on Generalization in Deep Learning
% There were a few posters at the C-BRIC JUMP meetings
% I gave a poster at the McGovern Institute retreat
% also one at the National Academy of Sciences at the 2019 Sackler Colloquium on Science of Deep Learning
	
    \vspace{15 pt}

    Emergent Abilities of Large Language Models? (Talk)
    \hfill
    Stanford IEEE
	\hfill % introduces  space to put words at the end
	\emph{Stanford, CA 2023}\\
	\vspace*{-3pt}
    
    Curse of low Task Diversity (Talk \& Poster)
    \hfill
    NeurIPS 2022
	\hfill % introduces  space to put words at the end
	\emph{New Orleans, LA, December 2022}\\
	\vspace*{-3pt}

    \vspace{5 pt}
    Compact, Fourier transform spectroscopy (Poster)
    \hfill
    Materials Day MIT
	\hfill % introduces  space to put words at the end
	\emph{Cambridge, MA, November 2018}\\
	\vspace*{-3pt}
    
    \vspace{5 pt}
    Theories of Deep Learning (Poster)
    \hfill
    MIT CBMM External Advisory Committee meeting
	\hfill % introduces  space to put words at the end
	\emph{Cambridge, MA, April 2018}\\
	\vspace*{-3pt}
	
	\vspace{5 pt}
    Theories of Deep Learning (Poster)
    \hfill
    MIT Quest for Intelligence launch
	\hfill % introduces  space to put words at the end
	\emph{Cambridge, MA, March 2018}\\
	\vspace*{-3pt}
	
	\vspace{5 pt}
    Theories of Deep Learning (Poster)
    \hfill
    MIT CBMM annual NSF meeting
	\hfill % introduces  space to put words at the end
	\emph{Cambridge, MA, March 2018}\\
	\vspace*{-3pt}
	
% 	\vspace{5 pt}
%     Guest presentation
%     \hfill
%     MIT course 9.520
% 	\hfill % introduces  space to put words at the end
% 	\emph{Cambridge, MA, November 2016}\\
% 	\vspace*{-3pt}
% 	\vspace{5 pt}
	
	\vspace{5 pt}
    % Training Hierarchical Networks for Function Approximation
    Thesis presentation
    \hfill
    Final M.Eng presentation MIT CBCL
	\hfill % introduces  space to put words at the end
	\emph{Cambridge, MA, August 2016}\\
	\vspace*{-3pt}
	
	\vspace{5 pt}
    Proxy for the Redis database
    \hfill
    Rackspace Final Internship Presentations
	\hfill % introduces  space to put words at the end
	\emph{San Antonio, TX, August 2014}\\
	\vspace*{-3pt}

	\vspace{5 pt}
    Sentiment Analysis presentation
    \hfill
    Adobe’s Engineering Department
	\hfill % introduces  space to put words at the end
	\emph{San Jose, CA, August 2013}\\
	\vspace*{-3pt}
    
% \begin{tabular}{ c c c }
%  Theories of Deep Learning (Poster) & MIT Quest for Intelligence launch & Cambridge, MA, March 2018 \\ 
%  Training Hierarchical Networks for Function Approximation & Final M.Eng presentation MIT CBCL & Cambridge, MA, August 2016 \\  
%  cell7 & cell8 & cell9    
% \end{tabular}
    
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Service

\header{Academic Service}

\begin{body}

\vspace{16pt}
\begin{itemize}
    \item ICLR 2020 (International Conference on Learning Representations) reviewer
    \item JMLR 2018 (Journal of Machine Learning Research) joint review with Qianli Liao
\end{itemize}

\end{body}

%%

\header{Service \& Outreach}

\begin{body}

\vspace{16pt}
\begin{itemize}
    \item Graduate advisor for Latinos in Computer Science (LCS) UIUC 2019-Present
    \item Outreach research mentorship Distributed Research Experiences for Undergraduates (DREU) UIUC 2019
    \item Outreach research mentorship Undergraduate Research Opportunity Program (UROP) MIT 2017-2018 
    \item Outreach research mentorship Engineering of Intelligence Team (EIT) CBMM MIT 2017-2018
\end{itemize}

\end{body}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching

\header{Teaching experience}
\begin{body}
	\vspace{16pt}
	
	\textbf{UIUC} - Urbana-Champaign, IL \hfill \emph{August 2020 - December 2020}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item \href{https://relate.cs.illinois.edu/course/CS446-fa20/}{CS 446 Machine Learning}
		\item Responsible for problem sets and exam design. Held weekly office hours.
	\end{itemize}
    
    \textbf{MIT CBMM} - Cambridge, MA \hfill \emph{September 2016 - December 2016}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Statistical Learning Theory \& Applications \href{http://www.mit.edu/~9.520/fall16/}{(9.520/6.860)} with professor Lorenzo Rosasco \& Tomaso Poggio
        \item Made the first draft of course slides for MIT's OpenCourseWare (OCW)
        \item Graded final projects
        \item Provided extra support for office hours
	\end{itemize}

   	\textbf{MIT EECS} - Cambridge, MA \hfill \emph{February 2016 - June 2016}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
        \item Introduction to Algorithms (6.006) with professor Nancy Lynch, Bruce Tidor and Aleksander Madry
        \item Held weekly office hours 
        \item Helped prepare problem sets and exams
        \item Graded exams
	\end{itemize}
    
   	\textbf{MIT EECS} - Cambridge, MA \hfill \emph{September 2015 - December 2015}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
        \item Design \& Analysis of Algorithms (6.046) with Shafi Goldwasser, Dana Moshkovitz, Nir N. Shavit
        \item Held weekly office hours
        \item Instructed students across weekly recitations
        \item Helped prepare problem sets and exams
	\end{itemize}
   
    \textbf{MIT EECS} - Cambridge, MA \hfill \emph{February 2015 - May 2015}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
        \item Introduction to Machine Learning (6.036) with professor Tommi S Jaakkola, Suvrit Sra \& Regina Barzilay
        \item Instructed students across bi-weekly recitations
        \item Held weekly office hours
        \item Helped prepare problem sets, projects and exams
        \item Graded problem sets, projects and exams
	\end{itemize}
    
    \textbf{MIT EECS} - Cambridge, MA \hfill \emph{September 2014 - December 2014}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Mathematics for Computer Science (6.042) with professor F.Thomson Leighton \& Ankur Moitra
        \item Instructed students across four recitations and problem solving sessions weekly
        \item Held weekly office hours
        \item Graded exams
	\end{itemize}
    
    \textbf{MIT} - Cambridge, MA \hfill \emph{September 2012 - June 2013}\\
	\emph{National Honor Society for Computer Science and Electrical Engineering (Eta Kappa Nu)}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Algorithms tutor for undergraduates at MIT 
	\end{itemize}

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Industry

\header{Industry experience}
\begin{body}
	\vspace{16pt}
    \textbf{Rackspace} - San Antonio, TX \hfill \emph{June 2014 - August 2014}\\
	\emph{Software Engineering Intern}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Built a concurrent proxy to extend the functionality of the Redis Database
        \item Added security functionality to the proxy
        \item Presented and delivered a demo to engineering team and higher level management
	\end{itemize}
   
   	\textbf{Adobe} - San Jose, CA \hfill \emph{June 2013 - August 2013}\\
	\emph{Software Engineering Intern}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Developed and optimized Machine Learning software for Sentiment Analysis in Spanish
        \item Researched different machine learning and natural language processing (NLP) techniques to optimize the Naive Bayes algorithm
        \item Developed different methods for automatic extraction of training data
        \item Presented and delivered a demo to Adobe's engineering department
	\end{itemize}

\end{body}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
\header{Projects}
\begin{body}
	\vspace{6pt}
	\begin{multicols}{2}
    
    	\textbf {Function approximation with deep Neural and Gaussian Networks}\\
		Masters of Engineering Thesis, advised by professor Tomaso Poggio \\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Researched the optimization landscape of Gaussian Networks with Gradient Descent
			\item Discovered a novel source of vanishing gradient impeding the training using backpropagation
		\end{itemize}
		\vspace{5pt}
        
        \textbf {Collaborative filtering for movie rating prediction}\\
		Matrix completion using mixture of Gaussians \\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Designed questions and solutions with fellow TA He Sun and professor Tommi S Jaakola
            \item Helped implement code that solved project with EM algorithm for matrix completion
		\end{itemize}
		\vspace{5pt}
        
        \textbf {Survey in Statistical Learning Theory}\\
		Graduate project for class 9.520/6.860 2014\\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Prepared a survey on Uniform Stability and Generalization in Learning theory
            \item Survey contained conceptual explanation to mathematical concepts in learning theory
            \item Survey also contained my own presentation of the proof for the theorems
			\item Survey can be read at: \href{https://www.quora.com/profile/Brando-Miranda/Posts/Uniform-Stability-and-Generalization-in-Learning-theory}{project report}
		\end{itemize}
		\vspace{5pt}
        
        \textbf {Survey in Theoretical Computer Science}\\
        Project for graduate class in mathematics 18.409 2015\\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Research paper survey on provable algorithms that require less computation time given more training examples
            \item In the case of SVM optimization PEGASOS requires less runtime assuming a target generalization
            \item When learning halfspaces over sparse vectors, more training examples reduce the training runtime from exponential to polynomial time
            \item Provided my unique outline of the main proof for halfspaces time reduction
		\end{itemize}
		\vspace{5pt}
        
        \textbf {Evaluating sublinear estimators for big data}\\
        undergraduate thesis project, advised by professor Samuel Madden \\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Designed sub-linear sampling algorithms for estimating groups from big data in databases
            \item Designed and proved that the algorithmic estimators were statistically consistency and unbiased
            \item Experimentally evaluated the algorithms with synthetic data sets using the Mean Absolute Percentage Error
		\end{itemize}
		\vspace{5pt}
	
		\textbf {Road Runner}\\
		Persistent, fault-tolerant, high-performance KV store \\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Built Multipaxos library for efficient consensus
			\item Optimized disk I/O with batching scheme
			\item Tested with mocks simulating RPC delays on unreliable, long-distance network
		\end{itemize}
		\vspace{5pt}
	
		\textbf {Dark Cloud}\\
		Secure, shared, cloud filesystem on untrusted server \\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Designed layered cryptography scheme
			\item Implemented the cryptography API
            \item Report: \href{https://css.csail.mit.edu/6.858/2013/projects/mpolanco-pcattori-brando90.pdf}{project report}
		\end{itemize}
		\vspace{5pt}
		
		\textbf {BattleCode} \\
		Artificial Intelligence competition\\
		\vspace*{-3pt}
		\begin{itemize} \itemsep -2pt
			\item Wrote path finding algorithms \& distributed combat strategy
			\item Finalists in competition pool of 300 teams
			\item Awarded \emph{Best Strategy Report}
		\end{itemize}
	\end{multicols}
\end{body}

%\medskip
%\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certification

\header{Certification}
\begin{body}
	\vspace{12pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item Coursera: Learning how to Learn: Powerful mental tools to help you master tough subjects (with Honors), awarded by UC San Diego, Dr. Barbara Oakley, Dr. Terrence Sejnowski \& Linda Walker
	\end{itemize}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item Coursera: Mindshift: Break Through Obstacles to Learning and Discover Your Hidden Potential (with Honors), by McMaster University Dr. Barbara Oakley, Dr. Terrence Sejnowski \& Linda Walker
	\end{itemize}
	\begin{itemize}
	    \item Certified Dance instructor with the World-Mastery program: completed the online training by world renowned artists Korke \& Judith
	\end{itemize}
% 	\begin{itemize} \itemsep -2pt  % reduce space between items
% 		\item Coursera: Creativity, Innovation, and Change, by Pennsylvania State University, Dr. Jablokow, Dr. Velegol, Dr. Matson et al. (under progress)
% 	\end{itemize}
%     \begin{itemize} \itemsep -2pt  % reduce space between items
%     \item Coursera: Synapses, Neurons and Brains, Hebrew University of Jerusalem, Dr. Idan Segev (under progress)
%     \end{itemize}
%     \vspace{14pt}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

\begin{body}
	\vspace{14pt}
	\emph{\textbf{Programming:}}{} Python, PyTorch, TensorFlow, JAX, Lean 4, OCaml, Coq, Java, Go, Javascript \\
	\smallskip
	\emph{\textbf{ML/AI Tools:}}{}  Hugging Face, Weights \& Biases, DSPy, git, UNIX, vim\\
	\smallskip
	\emph{\textbf{Languages:}}{} English, Spanish (both native fluency)\\
\end{body}
%\medskip
\smallskip

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\header{Leadership}

\begin{body}

    \vspace{16pt}

      \textbf{Stanford Research Mentor} - Stanford, CA \hfill \emph{September 2022 - Present}\\
	\emph{Research Mentor}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Research mentor with an undergraduate and two master's students on the role of data quality on the ability of Foundation Models to do in context learning. 
	\end{itemize}
	\vspace{5 pt}

	\textbf{Stanford AI for Lean (Lean AI Club)} - Stanford, CA \hfill \emph{2025 - Present}\\
	\emph{Founding Member}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Founding member of \href{https://aiforlean.org/}{Stanford AI for Lean}, a community of researchers and students dedicated to advancing AI for Lean theorem proving and formalizing mathematics
	\end{itemize}
	\vspace{5 pt}

 	\textbf{Stanford Bachata Sensual \& Brazilian Zouk (Latin Dance Group)} - Stanford, CA \hfill \emph{September 2021 - Present}\\
	\emph{President and Founder}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Founded the first Bachata Sensual \& Zouk (SBSBZ) dance group at the Stanford University -- and with our officers made it an officially recognized student organization
    	\item Lead weekly practice and dance classes for students and local community members. Communication channels have over 200 members.
    	\item In line with our commitment to providing accessible, zero-cost information to the wider community, we proudly offer comprehensive summaries of all our lessons on YouTube.
	\end{itemize}
	\vspace{5 pt}
    
    \textbf{UIUC Latinos in Computer Science (LCS)} - Urbana-Champaign, IL \hfill \emph{December 2019 - Present}\\
	\emph{Graduate Advisor}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Graduate advisor for Latinos in Computer Science (LCS)
    	\item Founded the ``LCS professional \& wellness development colloquium'' speaker series for LCS.
    	\item Organizing ``LCS professional \& wellness development colloquium'' speaker series for LCS.
    	Talks will be made available in the world wide web.
	\end{itemize}
	\vspace{5 pt}
	
	\textbf{UIUC Bachata Sensual \& Zouk (Latin Dance Group)} - Urbana-Champaign, IL \hfill \emph{January 2019 - December 2021}\\
	\emph{President and Founder}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Founded the first Bachata Sensual \& Zouk dance group at the UIUC campus
    	\item Lead weekly practice and dance classes for students and local community members
    	\item Organized first Bachata Sensual and Brazilian Zouk social with guest artist from Chicago
	\end{itemize}
	\vspace{5 pt}
	
	\textbf{UIUC Undergraduate Research Mentor} - Urbana-Champaign, IL \hfill \emph{May 2019 - Present}\\
	\emph{Research Mentor}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Research mentor for Research Experience for Undergraduates (REU).
    	\item Mentoring an undergraduate student on the foundations of meta-learning project.
	\end{itemize}
	\vspace{5 pt}
	
	\textbf{MIT CBMM (Center for Brain Minds \& Machines)} - Cambridge, MA \hfill \emph{June 2016 - May 2019}\\
	\emph{Research Mentor}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Research leader mentoring undergraduates with the Engineering of Intelligence Team \href{https://cbmm.mit.edu/eit/people}{(EIT)} at MIT CBMM
        \item Engaged in mentoring and research with MIT undergraduates
	\end{itemize}
	\vspace{5 pt}
	
	\textbf{MIT Student Latin Dance Group} - Cambridge, MA \hfill \emph{September 2015 - July 2017}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Lead an unofficial but committed student dance group under the guidance of MIT Casino Rueda
        \item Prepared and lead weekly dance practices
        \item Compiled a foundations Bachata dance curriculum
	\end{itemize}
	\vspace{5 pt}
	
	\textbf{Undergraduate Practice Opportunity Program (UPOP)} - Cambridge, MA \hfill \emph{January 2011 - June 2011}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Advanced professional skills with a one-week MIT intensive course and semester activities
        \item Advance "firm skills" through guided discovery learning, team decision-making, leadership skills, project engineering, cross cultural communication and recognizing the presence of an ethical dilemma with guidance of seasoned industry professionals and UPOP MIT faculty
	\end{itemize}
	\vspace{5 pt}

	\vspace{5pt}

\end{body}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Activities
\header{Activities}

\begin{body}
	\vspace{16pt}
    \textbf{MIT Chamber Music Society} - Cambridge, MA \hfill \emph{September 2011 - June 2014}\\
	\emph{Jazz Musician}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Alto Saxophone player with MIT's Jazz combo as part of the Chamber Music Society lead by Boston jazz artist 
		Keala Kaumeheiwa
        \item Performed, Composed and arranged several Jazz pieces
	\end{itemize}
	\vspace{5 pt}
    
    \textbf{MIT Wind Ensemble (MITWE)} - Cambridge, MA \hfill \emph{February 2011 - June 2011}\\
	\emph{Clarinetist}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Clarinet player with director Dr. Harris
        \item Performed with the Wind Ensemble at the MIT 150th Convocation 
	\end{itemize}
	\vspace{5 pt}
    
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Websites

% \header{Websites}
% \begin{body}
% 	\vspace{12pt}
% 	https://brando90.github.io/brandomiranda/
	
% 	https://cbmm.mit.edu/about/people/miranda

% 	https://www.linkedin.com/in/brando-miranda-40821046/
    
%     https://github.com/brando90
    
%     https://stackexchange.com/users/1589784/charlie-parker?tab=accounts
    
%     https://www.quora.com/profile/Brando-Miranda
    
% \end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Group Identity
\header{Family Background}

\begin{body}
	\vspace{12pt}
Latino/Hispanic, Mexican heritage.
\end{body}

%\medskip
\smallskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
%\header{Awards and Honors}

\end{document}
