\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage[hidelinks,pageanchor=false]{hyperref}
%\usepackage{href}


\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

%\usepackage[margin=0.0in]{geometry}
\usepackage{geometry}
 \geometry{
% a4paper,
 total={170mm,257mm},
 left=1in,
 top=20mm,
 }

% \leftmargin=0.25in
% \oddsidemargin=0.25in
% \textwidth=6.0in
% \topmargin=-0.25in
% \textheight=9.25in

\raggedright

% Even bottom margin across pages: stretch inter-paragraph glue
% rather than letting pages end short (default \raggedbottom).
% Publication entries use \\* (not \\) between title/authors/venue so
% LaTeX cannot insert a page break inside an entry — see CV margin rule.
\flushbottom
\widowpenalty=10000     % no widow lines (first line of paragraph at page bottom)
\clubpenalty=10000      % no orphan lines (last line of paragraph at page top)
\setlength{\parskip}{0pt plus 18pt}   % stretchable glue for \flushbottom to consume
\setlength{\parskip}{0pt plus 6pt}

\pagenumbering{gobble}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
	\nopagebreak[4]    % keep section content with its header (prevent orphan headers)
}

\newenvironment{body} {
		\vspace*{-16pt}
		\begin{changemargin}{-0.25in}{-0.5in}
	  }
		{\end{changemargin}\vspace{8pt plus 12pt}
	}

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

\newcommand{\tab}{\hspace*{2em}}

\newcommand{\bul}{$\bullet$ \hspace*{0em}}

\newcounter{pubnum}
\newcommand{\pubitem}{\stepcounter{pubnum}(\thepubnum)~}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{changemargin}{-0.5in}{-0.5in}
\begin{center}
{\Huge \bfseries Brando Miranda}\\
\vspace{8pt}
Gates Bldg., 353 Jane Stanford Way, Stanford, CA 94305\\
\textbf{brando9@stanford.edu}\\
\href{https://scholar.google.com/citations?user=_NQJoBkAAAAJ&hl=en}{Google Scholar} $\mid$
\href{https://brando90.github.io/brandomiranda/}{Website} $\mid$
\href{https://profiles.stanford.edu/brando-miranda}{Stanford Profile} $\mid$
\href{https://cbmm.mit.edu/about/people/miranda}{MIT CBMM Profile}
\end{center}
\vspace{8pt}
\end{changemargin}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interests
\header{Research Interests}

\begin{body}
\vspace{12pt}
AI for formal mathematics --- Lean 4 theorem proving, autoformalization, and end-to-end formal verification of software and mathematics; contamination-resistant evaluation of LLM mathematical reasoning; data-centric machine learning for foundation and frontier models; alternative architectures (e.g.\ energy-based models) toward Artificial General Intelligence.
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{12pt}
	\textbf{Ph.D. in Computer Science} \hfill \emph{2022-2026 (expected)}\\
	\emph{Stanford University}\\
	Advisor: Prof. Sanmi Koyejo, Stanford Trustworthy AI Research Group (STAIR).\\

	\smallskip
	\textbf{Master of Engineering in Electrical Engineering and Computer Science} \hfill \emph{2014-2016}\\
	\emph{Massachusetts Institute of Technology}\\
	Advisor: Prof. Tomaso Poggio, Center for Brains, Minds and Machines (CBMM).\\
	Thesis Title: \emph{Function Approximation with Deep Neural and Gaussian Networks}.\\

	\smallskip
	\textbf{Bachelor of Science, Computer Science and Engineering} \hfill \emph{2010-2014}\\
	\emph{Massachusetts Institute of Technology} \hfill \text{Minors: Mathematics, Music}\\
\end{body}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % Experience
% \header{Coursework}
%
% \begin{body}
% 	space{12pt}
% 	\begin{tabbing}
% 	\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm}\=\hspace*{1cm} \kill
% 	\bul Mathematical Logic \> \> \> \> \> \bul Programming Language Semantics \> \> \> \> \> \> \bul Formal Software Development Methods \\
% 	\bul Computability \& Complexity \> \> \> \> \> \bul Advances in Foundation Models \> \> \> \> \> \> \bul Algorithmic Aspects of Machine Learning \\
% 	\bul Artificial Intelligence \> \> \> \> \> \bul Statistical Learning Theory \> \> \> \> \> \> \bul Algorithms for Inference (PGMs) \\
% 	\bul Linear Algebra \> \> \> \> \> \bul Intro to Machine Learning \> \> \> \> \> \> \bul Online Methods in Machine Learning \\
% 	\bul Multi-variable Calculus \> \> \> \> \> \bul Probability \& Random Variables \> \> \> \> \> \> \bul Design \& Analysis of Algorithms \\
% 	\bul Differential Equations \> \> \> \> \> \bul Reinforcement Learning \& MDPs \> \> \> \> \> \> \bul Learning to Learn \\
% 	\bul Distributed Systems \> \> \> \> \> \bul Computer System Engineering \> \> \> \> \> \> \bul Computer System Security \\
% 	\end{tabbing}
% 	\end{body}
% %\medskip
% \smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Experience
\header{Professional Experience}

\begin{body}
	\vspace{12pt}

 	\textbf{Stanford University} - Stanford, CA \hfill \emph{September 2022 - 2026 (expected)}\\
	\emph{Ph.D. Student in Computer Science. Advisor: Professor Sanmi Koyejo}\\
	Research in AI for formal mathematics, Lean 4 verification benchmarks, contamination-resistant LLM evaluation, and data-centric machine learning for foundation models.\\
	\vspace{8pt}

	\textbf{MIT CBMM, UIUC \& Stanford} \hfill \emph{June 2016 - present}\\
	\emph{Research Mentor}\\
	Mentored undergraduate and graduate collaborators on data quality metrics, meta-learning, autoformalization, and formal verification; mentee projects led to ICLR, ICML, and NeurIPS workshop publications.\\
	\vspace{8pt}

	\textbf{Amazon Web Services (AWS)} - Cupertino, CA \hfill \emph{June 2024 - September 2024}\\
	\emph{Applied Scientist Intern}\\
	Applied LLMs to Lean 4 theorem proving and formal verification workflows.\\
	\vspace{8pt}

	\textbf{Morph Labs} - Remote \hfill \emph{October 2023 - December 2023}\\
	\emph{Machine Learning Research Scientist Consultant}\\
	Contributed to Morph Prover v0 7b and Moogle.ai, a search engine for verified Lean code.\\
	\vspace{8pt}

	\textbf{Wise Agents} - Stanford Spin-out \hfill \emph{2023}\\
	\emph{AI Research Consultant}\\
	Advised a Stanford spin-out on AI-agent workflows for sales-performance applications.\\
	\vspace{8pt}

	\textbf{IBM Research} - Yorktown Heights, NY \hfill \emph{May 2022 - August 2022}\\
	\emph{Graduate Research Intern}\\
	Conducted machine-learning research for program synthesis.\\
	\vspace{8pt}

	\textbf{University of Illinois Urbana-Champaign} - Urbana-Champaign, IL \hfill \emph{September 2018 - May 2022}\\
	\emph{Graduate Student. Advisor: Professor Sanmi Koyejo}\\
	Research on meta-learning, task diversity, data diversity, and evaluation methodology.\\
	\vspace{8pt}

	\textbf{IBM Research} - Yorktown Heights, NY \hfill \emph{May 2021 - August 2021}\\
	\emph{Graduate Research Intern}\\
	Conducted machine-learning research in program synthesis and code generation.\\
	\vspace{8pt}

	\textbf{MIT CBMM (Center for Brain Minds \& Machines)} - Cambridge, MA \hfill \emph{June 2015 - September 2018}\\
	\emph{Research Assistant. Advisor: Professor Tomaso Poggio}\\
	Deep-learning theory and generalization research, including IJAC and ICML workshop publications.\\
	\vspace{8pt}

	\textbf{Rackspace} - San Antonio, TX \hfill \emph{June 2014 - August 2014}\\*
	\emph{Software Engineering Intern}\\*
	Built a concurrent Redis proxy with additional security functionality.\\
	\vspace{8pt}

	\textbf{Adobe} - San Jose, CA \hfill \emph{June 2013 - August 2013}\\*
	\emph{Software Engineering Intern --- ML/NLP for Spanish Sentiment Analysis}\\*
	Developed NLP methods for Spanish sentiment analysis, including negation handling and automatic training-data extraction.\\

 %        \textbf{MIT (Undergraduate Research Opportunity Program)} - Cambridge, MA \hfill \emph{June 2012 - August 2012}\\
	% \emph{Undergraduate Research Assistant}\\
	% \vspace*{-3pt}
	% \begin{itemize} \itemsep -2pt
	% 	\item Project: Crowd-Sourcing the Design of Drug-Delivery Vehicles for Cancer Treatment
 %        \item Developed user interface (UI) that enables the general population to design drug delivery vehicles for cancer treatment
 %        \item Built the communication network allowing reliable interaction amongst the user interface, database and back-end of the project
 %        \item Presented and explained the project to the research lab.
	% \end{itemize}
    
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Artifacts & Systems
\header{Research Artifacts \& Systems}

\begin{body}
	\vspace{12pt}
	\begin{itemize} \itemsep -2pt
		\item \textbf{VeriBench}: End-to-end Lean 4 benchmark for evaluating AI-generated code with formal verification proofs.
		\item \textbf{Putnam-AXIOM}: Functional and static benchmark for higher-level LLM mathematical reasoning.
		\item \textbf{Pantograph}: Machine-to-machine interface for Lean 4 theorem proving, reasoning, and data extraction.
		\item \textbf{Morph Prover v0 7b and Moogle.ai}: Lean 4 proof model and search engine for verified Lean code developed with Morph Labs.
	\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
\header{Publications}
\begin{body}
    \vspace{6pt} % DONT REMOVE THIS

    \vspace{8pt}
    \emph{Google Scholar metrics (as of May 14, 2026): 3,014+ citations | h-index: 17 | i10-index: 22.}

    \vspace{8pt}
    \textbf{Refereed Publications}
    \par\nopagebreak[4]\vspace{4pt}
    \setcounter{pubnum}{0}

    \pubitem \href{https://openreview.net/forum?id=vdXPorr099}
    {E. Chen, A. Gulati, \textbf{B. Miranda}, Z. Tang, S. Koyejo,
    \emph{Rethinking LLM Judges: Chain-of-Thought and Multi-Step Pipelines for Math Grading}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Workshop on Logical Reasoning of Large Language Models. 2026})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=8OoZ8dnvIT}
    {Z. Zhou, X. Lu, C. Cao, \textbf{B. Miranda}, T. Liu, B. Han, S. Koyejo,
    \emph{CoDaPO: Confidence and Difficulty-Adaptive Policy Optimization for LLM Reasoning}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Workshop on Lifelong Agents: Learning, Aligning, Evolving. 2026} \& \textbf{2nd Workshop on AI for Math at International Conference on Machine Learning (ICML). 2025})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/pdf/2406.04391}
    {R. Schaeffer, H. Schoelkopf, \textbf{B. Miranda}, G. Mukobi, V. Madan, A. Ibrahim, H. Bradley, S. Biderman, S. Koyejo,
    \emph{Why Has Predicting Downstream Capabilities of Frontier AI Models with Scale Remained Elusive?}.}
    \\*
    (\textbf{International Conference on Machine Learning (ICML). 2025} \& \textbf{International Conference on Machine Learning (ICML) Workshop on Trustworthy Multi-modal Foundation Models and AI Agents (TiFA). 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2508.08292}
    {A. Gulati, \textbf{B. Miranda}, E. Chen, E. Xia, K. Fronsdal, B. de Moraes Dumont, S. Koyejo,
    \emph{Putnam-AXIOM: A Functional \& Static Benchmark for Measuring Higher Level Mathematical Reasoning in LLMs}.}
    \\*
    (\textbf{International Conference on Machine Learning (ICML). 2025} \& \textbf{Neural Information Processing Systems (NeurIPS) Workshop on Mathematics and AI (MATH-AI). 2024})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=rWkGFmnSNl}
    {\textbf{B. Miranda}, Z. Zhou, A. Nie, E. Obbad, L. Aniva, K. Fronsdal, W. Kirk, D. Soylu, et al.,
    \emph{VeriBench: End-to-End Formal Verification Benchmark for AI Code Generation in Lean 4}.}
    \\*
    (\textbf{2nd Workshop on AI for Math at International Conference on Machine Learning (ICML). 2025})

    \vspace{10pt}
    \pubitem \href{https://link.springer.com/chapter/10.1007/978-3-031-90643-5_6}
    {L. Aniva, C. Sun, \textbf{B. Miranda}, C. Barrett, S. Koyejo,
    \emph{Pantograph: A machine-to-machine interaction interface for advanced theorem proving, high level reasoning, and data extraction in Lean 4}.}
    \\*
    (\textbf{International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS). 2025})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2601.04301}
    {R. Schaeffer, J. Kazdan, B. Abbasi, K. Z. Liu, \textbf{B. Miranda}, A. M. Ahmed, F. Berez, et al.,
    \emph{Quantifying the Effect of Test Set Contamination on Generative Evaluations}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS) Workshop on Evaluating the Evolving LLM Lifecycle. 2025})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2506.19882}
    {R. Schaeffer, J. Kazdan, Y. Denisov-Blanch, \textbf{B. Miranda}, M. Gerstgrasser, et al.,
    \emph{Position: Machine Learning Conferences Should Establish a `Refutations and Critiques' Track}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS), Main Track. 2025})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=wDjOpXKgtU}
    {S. Barkallah, S. Daruru, \textbf{B. Miranda}, L. Aniva, A. Nie, S. Koyejo,
    \emph{VeriBench-FTP: A Formal Theorem Proving Benchmark in Lean 4 for Code Verification}.}
    \\*
    (\textbf{5th Neural Information Processing Systems (NeurIPS) Workshop on Mathematical Reasoning and AI. 2025})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=Ajr8YtfhVO}
    {R. Schaeffer, K. Liu, \textbf{B. Miranda}, A. M. Ahmed, N. Mireshghallah, S. Koyejo,
    \emph{The Contamination Paradox: Why Test Set Leakage Can Be Both Potent and Negligible}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS) Workshop on Evaluating the Evolving LLM Lifecycle. 2025})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=wvFnqVVUhN}
    {R. Schaeffer, D. Valentine, L. Bailey, J. Chua, et al., \textbf{B. Miranda}, et al., S. Koyejo, E. Perez,
    \emph{Failures to Find Transferable Image Jailbreaks Between Vision-Language Models}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR). 2024} \& \textbf{Neural Information Processing Systems (NeurIPS) Workshop on Red Teaming Generative AI. 2024})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=f6IB0WrOKS}
    {R. Schaeffer, M. Khona, S. Chandra, M. Ostrow, \textbf{B. Miranda}, S. Koyejo,
    \emph{Does Maximizing Neural Regression Scores Teach Us About The Brain?}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS) Workshop on Unifying Representations in Neural Models (UniReps), 2nd Edition. 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2501.08496}
    {K. Chawla, A. Sahai, M. DePavia, S. Sundar, \textbf{B. Miranda},
    \emph{Quantifying the Importance of Data Alignment in Downstream Model Performance}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Workshop on Data-Centric Machine Learning Research (DMLR). 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2406.06555}
    {A. Gulati, D. Ladsaria, S. Mishra, J. Sidhu, \textbf{B. Miranda},
    \emph{An Evaluation Benchmark for Autoformalization in Lean4}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Tiny Papers Track, Second Edition. 2024})

    \vspace{10pt}
    \pubitem {K. Chawla, A. Sahai, M. DePavia, \textbf{B. Miranda},
    \emph{A Systematic Study of the Role of Data Quality and Alignment for Fine-tuning LLMs for Enhanced Autoformalization}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Tiny Papers Track, Second Edition. 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2304.15004}
    {R. Schaeffer, \textbf{B. Miranda}, S. Koyejo,
    \emph{Are Emergent Abilities of Language Models a Mirage?}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS), Main Track. 2023})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2306.13840}
    {\textbf{B. Miranda}*, A. Lee*, P. Yu, S. Koyejo,
    \emph{Beyond Scale: the Diversity Coefficient as a Data Quality Metric Demonstrates LLMs are Pre-trained on Formally Diverse Data}.}
    \\*
    (\textbf{International Conference on Machine Learning (ICML) Workshop on Data-Centric Machine Learning. 2023} \& \textbf{International Conference on Machine Learning (ICML) Workshop on Deployable Generative AI. 2023}) (*equal contribution)

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2208.01545}
    {\textbf{B. Miranda}, P. Yu, Y. Wang, S. Koyejo,
    \emph{The Curse of Zero Task Diversity: the Failure of Transfer Learning to Outperform MAML and their Empirical Equivalence}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS) Workshop on Meta-Learning. 2022})

    \vspace{10pt}
    \pubitem \href{https://cbmm.mit.edu/publications/weight-and-batch-normalization-implement-classical-generalization-bounds}
    {T. Poggio, A. Banburski, Q. Liao, \textbf{B. Miranda}, L. Rosasco, J. Hidary,
    \emph{Weight and Batch Normalization implement Classical Generalization Bounds}.}
    \\*
    (\textbf{International Conference on Machine Learning (ICML) Workshop. 2019})

    \vspace{10pt}
    \pubitem \href{https://opg.optica.org/abstract.cfm?uri=cleo_si-2018-SF1A.1}
    {D. Kita, \textbf{B. Miranda}, H. Lin, J. Michon, D. Favela, J. Hu,
    \emph{High-resolution on-chip digital Fourier transform spectroscopy}.}
    \\*
    (\textbf{Conference on Lasers and Electro-Optics (CLEO): Science and Innovations. 2018})

    \vspace{10pt}
    \pubitem \href{https://www.nature.com/articles/s41467-018-06773-2}
    {D. Kita, \textbf{B. Miranda}, D. Favela, D. Bono, J. Michon, H. Lin, T. Gu, J. Hu,
    \emph{High-performance and scalable on-chip digital Fourier transform spectroscopy}.}
    \\*
    (\textbf{Nature Communications 9 (1), 4405. 2018})

    \vspace{10pt}
    \pubitem \href{https://link.springer.com/article/10.1007/s11633-017-1054-2}
    {T. Poggio, H. Mhaskar, L. Rosasco, \textbf{B. Miranda}, Q. Liao,
    \emph{Why and when can deep-but not shallow-networks avoid the curse of dimensionality: A review}.}
    \\*
    (\textbf{International Journal of Automation and Computing (IJAC). 2017})

    \vspace{12pt}
    \textbf{Preprints and Technical Reports}
    \par\nopagebreak[4]\vspace{4pt}
    \setcounter{pubnum}{0}

    \pubitem \href{https://cs.stanford.edu/~daneshva/publications/ai-coding-benchmarks-need-proofs-not-just-tests.pdf}
    {D. Amrollahi, M. Karimi, \textbf{B. Miranda}, L. Aniva, C. Sun, C. Barrett, S. Koyejo,
    \emph{AI Coding Benchmarks Need Proofs, Not Just Tests}.}
    \\*
    (\textbf{Preprint 2026})

    \vspace{10pt}
    \pubitem {E. Obbad, \textbf{B. Miranda}, D. L. W. Hall, R. Schaeffer, S. Koyejo, P. Liang,
    \emph{Curating High Quality Pretraining Data for Language Models via Compression Ratios}.}
    \\*
    (\textbf{Preprint 2026})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2510.06261}
    {Z. Zhou, C. Cao, X. Feng, X. Li, Z. Li, X. Lu, J. Yao, W. Huang, T. Cheng, et al., \textbf{B. Miranda},
    \emph{AlphaApollo: Orchestrating Foundation Models and Professional Tools into a Self-Evolving System for Deep Agentic Reasoning}.}
    \\*
    (\textbf{Preprint 2025, arXiv:2510.06261})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2509.24012}
    {R. Schaeffer, N. Levi, \textbf{B. Miranda}, S. Koyejo,
    \emph{Pretraining Scaling Laws for Generative Evaluations of Language Models}.}
    \\*
    (\textbf{Preprint 2025, arXiv:2509.24012})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2509.23963}
    {R. Schaeffer, N. Levi, A. Kirsch, T. Guenais, \textbf{B. Miranda}, E. Obbad, S. Koyejo,
    \emph{Evaluating the Robustness of Chinchilla Compute-Optimal Scaling}.}
    \\*
    (\textbf{Preprint 2025, arXiv:2509.23963})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2502.15795}
    {W. Chan, M. Souliman, J. Nordhagen, \textbf{B. Miranda}, E. Obbad, S. Koyejo,
    \emph{Lean-ing on Quality: How High-Quality Data Beats Diverse Multilingual Data in Autoformalization}.}
    \\*
    (\textbf{Preprint 2025, arXiv:2502.15795})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2501.08506}
    {K. Selva, S. Vittayaareekul, \textbf{B. Miranda},
    \emph{Exploring the Efficacy of Meta-Learning: Unveiling Superior Data Diversity Utilization of MAML Over Pre-training}.}
    \\*
    (\textbf{Preprint 2025, arXiv:2501.08506})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2410.18194}
    {E. Obbad, I. Mlauzi, \textbf{B. Miranda}, R. Schaeffer, K. Obbad, S. Bedi, S. Koyejo,
    \emph{ZIP-FIT: Embedding-Free Data Selection via Compression-Based Alignment}.}
    \\*
    (\textbf{Preprint, arXiv 2024})

    \vspace{10pt}
    \pubitem {J. Rotella, Z. Qin, A. Z. H. Yang, \textbf{B. Miranda}, M. E. A. Seddik, J. Zuo, H. Hacid, et al.,
    \emph{Synthetic Theorem Generation in Lean}.}
    \\*
    (\textbf{Preprint 2024})

    \vspace{10pt}
    \pubitem \href{https://huggingface.co/typeof/morph-prover-v0-7b-sharded}
    {\textbf{B. Miranda} (ML Research Scientist Consultant) \& Morph Labs Team,
    \emph{Morph Prover v0 7b: The 1st Frontier Model for the Lean 4 Formal Verification Programming Language}.}
    \\*
    (\textbf{Technical Report and Model Card. 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2306.13841}
    {\textbf{B. Miranda}, P. Yu, S. Goyal, Y. Wang, S. Koyejo,
    \emph{Is Pre-training Truly Better Than Meta-Learning?}.}
    \\*
    (\textbf{Preprint 2023})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2304.10500}
    {\textbf{B. Miranda}, A. Shinnar, V. Pestun, B. Trager,
    \emph{Transformer Models for Type Inference in the Simply Typed Lambda Calculus: A Case Study in Deep Learning for Code}.}
    \\*
    (\textbf{Preprint 2023})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2112.13137}
    {\textbf{B. Miranda}, Y. Wang, S. Koyejo,
    \emph{Does MAML Only Work via Feature Re-use? A Data Set Centric Perspective}.}
    \\*
    (\textbf{Preprint 2021})

    \vspace{10pt}
    \pubitem \href{https://www.ideals.illinois.edu/handle/2142/109139}
    {\textbf{B. Miranda},
    \emph{An Empirical Study of Meta-Learning: a step towards rigorously understanding meta-learning algorithms}.}
    \\*
    (\textbf{Preprint 2020})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/1903.04991}
    {A. Banburski, Q. Liao, \textbf{B. Miranda}, L. Rosasco, B. Liang, J. Hidary, T. Poggio,
    \emph{Theory III: Dynamics and Generalization in Deep Networks}.}
    \\*
    (\textbf{Preprint 2019})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/1807.09659}
    {Q. Liao, \textbf{B. Miranda}, A. Banburski, J. Hidary, T. Poggio,
    \emph{A Surprising Linear Relationship Predicts Test Performance in Deep Networks}.}
    \\*
    (\textbf{Preprint 2018})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/1801.02254}
    {C. Zhang, Q. Liao, A. Rakhlin, \textbf{B. Miranda}, N. Golowich, T. Poggio,
    \emph{Theory of Deep Learning IIb: Optimization Properties of SGD}.}
    \\*
    (\textbf{Preprint 2018})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/1806.11379}
    {T. Poggio, Q. Liao, \textbf{B. Miranda}, A. Banburski, X. Boix, J. Hidary,
    \emph{Theory IIIb: Generalization in Deep Networks}.}
    \\*
    (\textbf{Preprint 2018})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/1801.00173}
    {T. Poggio, K. Kawaguchi, Q. Liao, \textbf{B. Miranda}, L. Rosasco, X. Boix, J. Hidary, M. Mhaskar,
    \emph{Theory of Deep Learning III: explaining the non-overfitting puzzle}.}
    \\*
    (\textbf{Preprint 2017})

    \vspace{6pt}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards & Honors

\header{Awards \& Honors}
\begin{body}
\vspace{12pt}
\begin{itemize} \itemsep -2pt
    \item \textbf{ICML 2026 Silver Reviewer} (May 2026) --- top reviewer recognition signed by the ICML 2026 Program Chairs.
    \item \textbf{Oral Recommendation (Top 1)}, 2nd AI for Math Workshop @ ICML 2025 --- for \textit{VeriBench: End-to-End Formal Verification Benchmark for AI Code Generation in Lean 4} (Miranda et al.); reviewer recommendation ``Accept (Oral, Top 1)''.
    \item \textbf{Pear AI Researchers Circle} (July 2025) --- selective AI-researcher network convened by Pear VC; invited following the final round (R3) of the Pear AI Researcher Grant program.
    \item \textbf{ICML Workshop on Trustworthy Multi-modal Foundation Models and AI Agents (TiFA) --- Outstanding Paper Award} (July 2024) --- for ``Why Has Predicting Downstream Capabilities of Frontier AI Models with Scale Remained Elusive?'' (Schaeffer, Schoelkopf, Miranda, et al.).
    \item \textbf{NeurIPS Outstanding Main Track Paper Award} (December 2023) --- top 0.4\% of NeurIPS submissions; only 2 main-track papers selected. For ``Are Emergent Abilities of Large Language Models a Mirage?'' (Schaeffer, Miranda, Koyejo).
    \item \textbf{EDGE Scholar}, Stanford University (September 2022) --- Stanford fellowship supporting first-generation / low-income PhD students with additional mentorship and stipend.
    \item \textbf{Stanford School of Engineering Fellowship} (September 2022) --- multi-year departmental fellowship for incoming Stanford engineering PhD students.
    \item \textbf{Honorable Mention, Ford Foundation Predoctoral Fellowship} (2020, 2021) --- national fellowship recognizing PhD applicants with potential to diversify the U.S. professoriate.
    \item \textbf{Best Research Project Award}, UIUC graduate course CS 598 ``Learning to Learn'' (Prof. Y. Wang, December 2020) --- course-level award for the top research project.
    \item \textbf{HSF Scholar}, Hispanic Scholarship Fund (2020) --- competitive national merit fellowship for Hispanic graduate students.
    \item \textbf{Computer Science Excellence Saburo Muroga Endowed Fellowship}, UIUC (2019-2020) --- top departmental fellowship for outstanding incoming CS PhD students.
    \item \textbf{Most Cited Paper Certificate}, International Journal of Automation \& Computing (IJAC, December 2019) --- for ``Why and when can deep- but not shallow-networks avoid the curse of dimensionality: a review'' (Poggio, Mhaskar, Rosasco, Miranda, Liao).
    \item \textbf{Sloan Scholar}, Alfred P. Sloan Foundation Minority Ph.D. (MPHD) Program (2018-2019) --- prestigious national fellowship supporting underrepresented STEM PhD students.
    \item \textbf{Grainger Engineering SURGE Fellowship}, UIUC (2018-2019) --- multi-year college-level fellowship for diverse engineering PhD students.
		\item \textbf{MIT Mitchell B. Kaufman Memorial Scholarship} (2012-2013, 2013-2014) --- MIT undergraduate scholarship support.
		\item \textbf{MIT Eugene and Margaret McDermott Scholarship} (2012-2013, 2013-2014) --- MIT undergraduate scholarship support.
	\item \textbf{Chopper Trading, LLC, Best Strategy Report Award}, MIT BattleCode AI competition (2013) --- top finisher among $\sim$300 teams.
	 	\item \textbf{Greengates Scholarship} (30\% 2007, 50\% 2008, 100\% 2009, 100\% 2010) --- merit scholarship that increased to full-tuition support.
	\item \textbf{High Achievement Prize Award}, Greengates School (2007, 2008, 2009, 2010) --- equivalent to Valedictorian.
		\item \textbf{Best All-Round Student Award}, Greengates School (2010) --- school-wide award recognizing the top all-around student.
		\item \textbf{Achievement Prize Award}, Greengates School (2006) --- school recognition for academic achievement.
		\item \textbf{Certificate for Progress Award}, Greengates School (2005) --- school recognition for academic progress.
\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Media Coverage

\header{Media Coverage}
\begin{body}
\vspace{12pt}
\begin{itemize} \itemsep -2pt
    \item \textbf{Hacker News / Y Combinator (2025)}: \href{https://news.ycombinator.com/item?id=42565606}{Putnam-AXIOM benchmark posted on Hacker News} --- the \textit{Putnam-AXIOM} benchmark for higher-level LLM mathematical reasoning drew front-page attention on Y Combinator's influential tech-news forum
    \item \textbf{White House Economic Report of the President (2024)}: Miranda et al.'s work on emergent abilities was cited in the 2024 Economic Report of the President -- the White House's annual flagship document on national economic policy
    \item \textbf{Quanta Magazine (2024)}: ``How Quickly Do Large Language Models Learn Unexpected Skills?''
    \item \textbf{Andrew Ng (2024)}: Endorsed the emergent-abilities paper as evidence that AGI development will be smooth and predictable
    \item \textbf{The New York Times (2023)}: ``Silicon Valley Confronts the Idea That the `Singularity' Is Here''
    \item \textbf{Forbes (2023)}: ``AI `Emergent Abilities' Are A Mirage, Says AI Researcher''
    \item \textbf{AK / @\_akhaliq on X (2023)}: \href{https://x.com/_akhaliq/status/1673507375515594766}{AK shared the \textit{Beyond Scale} paper on X} --- the influential AI-research-paper aggregator (Gradio founder; now at HuggingFace) tweeted the \textit{Beyond Scale} data-diversity paper to his large research audience (68.9K views)
    \item \textbf{Stanford AI Lab Blog (ICML 2023)}: \href{https://ai.stanford.edu/blog/icml-2023/}{The \textit{Beyond Scale} and \textit{Is Pre-training Truly Better Than Meta-Learning?} papers were featured in the Stanford AI Lab blog roundup of ICML 2023}
    \item \textbf{Additional coverage}: Stanford HAI, Y Combinator News, Vice, Medium, HackerNews, NeurIPS blog, Reddit
\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Invited & Contributed Talks

\header{Invited \& Contributed Talks}

\begin{body}
    \vspace{12pt}

    \textbf{Applications of Trustworthy Machine Reasoning with AI Coding Agents}\\*
    \href{https://trustworthy-machine-reasoning.github.io/}{AAAI 2026 Tutorial} ``Trustworthy Machine Reasoning with Foundation Models'' (Part IV, 50 min). Co-presented with B. Han, Z. Zhou, C. Cao, P. Lu, S. Koyejo. \emph{Singapore, January 20, 2026.}

    \vspace{8pt}
    \textbf{Emergent Abilities in Large Language Models: Mirage or an Elusive Predictive Frontier?}\\*
    Hong Kong Baptist University, Department of Computer Science Seminar (2026 Series). \emph{Hong Kong, January 19, 2026.}

    \vspace{8pt}
    \textbf{VeriBench: End-to-End Formal Verification Benchmark for AI Code Generation in Lean 4}\\*
    \href{https://docs.google.com/presentation/d/11w7Q9wbfimfs0e87XuLagkhj7Q1lk8Wq-ASM-xJVHdg/edit?usp=sharing}{Lawrence Livermore National Laboratory Reading Group} (invited). \emph{July 31, 2025.}

    \vspace{8pt}
    \textbf{Intro to Lean 4, VeriBench, and Trustworthy Testing of AI-Generated Code}\\*
    \href{https://docs.google.com/presentation/d/1KRBym-sOORaxszOJQHdD4u80wAl7jHy8Pda0KAcdeZw/edit?usp=sharing}{Prof. Azalia Mirhoseini's Lab Meeting, Stanford} (invited). \emph{2025.}

    \vspace{8pt}
    \textbf{Failures to Find Transferable Image Jailbreaks Between Vision-Language Models}\\*
    NeurIPS Red Teaming GenAI Workshop, Contributed Talk. \emph{December 2024.}

    \vspace{8pt}
    \textbf{Are Emergent Abilities of Large Language Models a Mirage?}\\*
    Stanford IEEE Invited Talk. \emph{Stanford, CA, 2023.}

    \vspace{8pt}
    \textbf{Are Emergent Abilities of Large Language Models a Mirage? --- Why Has Predicting Downstream Capabilities Remained Elusive?}\\*
    \href{https://docs.google.com/presentation/d/1cr_X6jzZxShHMUVjzHAkitCnPZCbBfyxxxgZg8S90SI/edit?usp=sharing}{Lawrence Livermore National Laboratory} (invited talk). \emph{2023.}

    \vspace{8pt}
    \textbf{Emergent Abilities of Large Language Models}\\*
    \href{https://docs.google.com/presentation/d/1UDqPg06xQKga1oWSEMS2jyzignQwkot6ZbjQMhdZngs/edit?usp=sharing}{Amazon Research} (invited talk). \emph{2023.}

    \vspace{8pt}
    \textbf{The Curse of Low Task Diversity: On the Failure of Transfer Learning to Outperform MAML and Their Empirical Equivalence}\\*
    NeurIPS Meta-Learning Workshop, Contributed Talk. \emph{New Orleans, LA, December 2022.}

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Selected Writing
\header{Selected Writing}

\begin{body}
	\vspace{12pt}
	\begin{itemize} \itemsep -2pt
		\item \textbf{\href{https://brando90.github.io/brandomiranda/2026/04/22/formal-methods-scalable-oversight.html}{Asking the Right Question: Formal Methods as Scalable Oversight}} \hfill \emph{April 2026}
		\item \textbf{\href{https://brando90.github.io/brandomiranda/2026/04/13/correctness-gated-multi-agent-workflow.html}{Building a Correctness-Gated Multi-Agent Workflow for Research}} \hfill \emph{April 2026}
	\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Service

\header{Academic Service}

\begin{body}

\vspace{12pt}
\begin{itemize}
    \item \textbf{NeurIPS 2026} (Neural Information Processing Systems) Conference reviewer
    \item \textbf{ICLR 2026} (International Conference on Learning Representations) Conference reviewer
    \item \textbf{ICML 2026} (International Conference on Machine Learning) Conference reviewer -- \textbf{Silver Reviewer designation} (top reviewer recognition)
    \item \textbf{ICLR 2025} (International Conference on Learning Representations) Conference reviewer
    \item \textbf{ICML 2025} 2nd AI for Math (AI4MATH) Workshop reviewer
    \item \textbf{ICLR 2024} Data-centric Machine Learning Research (DMLR) Workshop reviewer
    \item \textbf{NeurIPS 2023} Mathematical Reasoning and AI (MATH-AI) Workshop reviewer
    \item \textbf{ICLR 2020} (International Conference on Learning Representations) Conference reviewer
    \item \textbf{JMLR 2018} (Journal of Machine Learning Research) joint review with Qianli Liao
\end{itemize}

\end{body}

%%

\header{Service \& Outreach}

\begin{body}

\vspace{12pt}
\begin{itemize}
    \item Graduate advisor for Latinos in Computer Science (LCS) UIUC 2019-Present
    \item Outreach research mentorship Distributed Research Experiences for Undergraduates (DREU) UIUC 2019
    \item Outreach research mentorship Undergraduate Research Opportunity Program (UROP) MIT 2017-2018 
    \item Outreach research mentorship Engineering of Intelligence Team (EIT) CBMM MIT 2017-2018
\end{itemize}

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching

\newpage
\header{Teaching experience}
\begin{body}
	\vspace{12pt}

	\textbf{Stanford University} - Stanford, CA \hfill \emph{2023 - 2025}\\
	\emph{Course Assistant (3 quarters) \& Instructor of Record (Spring)}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item CS 197 \textit{How to Do CS Research} with Prof. Michael Bernstein --- TA'd 3 quarters; served as \textbf{Instructor of Record} for the Spring offering
		\item Mentored undergraduate research projects from the course that produced \textbf{2 workshop publications} (including ICML workshop tracks)
	\end{itemize}

	\textbf{UIUC} - Urbana-Champaign, IL \hfill \emph{August 2020 - December 2020}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item \href{https://relate.cs.illinois.edu/course/CS446-fa20/}{CS 446 Machine Learning}
		\item Responsible for problem sets and exam design. Held weekly office hours.
	\end{itemize}
    
    \textbf{MIT CBMM} - Cambridge, MA \hfill \emph{September 2016 - December 2016}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Statistical Learning Theory \& Applications \href{http://www.mit.edu/~9.520/fall16/}{(9.520/6.860)} with professor Lorenzo Rosasco \& Tomaso Poggio
        \item Made the first draft of course slides for MIT's OpenCourseWare (OCW)
        \item Graded final projects
        \item Provided extra support for office hours
	\end{itemize}

   	\textbf{MIT EECS} - Cambridge, MA \hfill \emph{February 2016 - June 2016}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
        \item Introduction to Algorithms (6.006) with professor Nancy Lynch, Bruce Tidor and Aleksander Madry
        \item Held weekly office hours 
        \item Helped prepare problem sets and exams
        \item Graded exams
	\end{itemize}
    
   	\textbf{MIT EECS} - Cambridge, MA \hfill \emph{September 2015 - December 2015}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
        \item Design \& Analysis of Algorithms (6.046) with Shafi Goldwasser, Dana Moshkovitz, Nir N. Shavit
        \item Held weekly office hours
        \item Instructed students across weekly recitations
        \item Helped prepare problem sets and exams
	\end{itemize}
   
    \textbf{MIT EECS} - Cambridge, MA \hfill \emph{February 2015 - May 2015}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
        \item Introduction to Machine Learning (6.036) with professor Tommi S Jaakkola, Suvrit Sra \& Regina Barzilay
        \item Instructed students across bi-weekly recitations
        \item Held weekly office hours
        \item Helped prepare problem sets, projects and exams
        \item Graded problem sets, projects and exams
	\end{itemize}
    
    \textbf{MIT EECS} - Cambridge, MA \hfill \emph{September 2014 - December 2014}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Mathematics for Computer Science (6.042) with professor F.Thomson Leighton \& Ankur Moitra
        \item Instructed students across four recitations and problem solving sessions weekly
        \item Held weekly office hours
        \item Graded exams
	\end{itemize}
    
    \textbf{MIT} - Cambridge, MA \hfill \emph{September 2012 - June 2013}\\
	\emph{National Honor Society for Computer Science and Electrical Engineering (Eta Kappa Nu)}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item Algorithms tutor for undergraduates at MIT
	\end{itemize}

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Industry (moved into Professional Experience above)
%
%\header{Industry experience}
%\begin{body}
%	\vspace{12pt}
%    \textbf{Rackspace} - San Antonio, TX \hfill \emph{June 2014 - August 2014}\\
%	\emph{Software Engineering Intern}\\
%	\vspace*{-3pt}
%	\begin{itemize} \itemsep -2pt
%		\item Built a concurrent proxy to extend the functionality of the Redis Database
%        \item Added security functionality to the proxy
%        \item Presented and delivered a demo to engineering team and higher level management
%	\end{itemize}
%
%   	\textbf{Adobe} - San Jose, CA \hfill \emph{June 2013 - August 2013}\\
%	\emph{Software Engineering Intern}\\
%	\vspace*{-3pt}
%	\begin{itemize} \itemsep -2pt
%		\item Developed and optimized Machine Learning software for Sentiment Analysis in Spanish
%        \item Researched different machine learning and natural language processing (NLP) techniques to optimize the Naive Bayes algorithm
%        \item Developed different methods for automatic extraction of training data
%        \item Presented and delivered a demo to Adobe's engineering department
%	\end{itemize}
%
%\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
%\header{Projects}
%\begin{body}
%	\vspace{8pt}
%	\begin{multicols}{2}
%    
%    	\textbf {Function approximation with deep Neural and Gaussian Networks}\\
%		Masters of Engineering Thesis, advised by professor Tomaso Poggio \\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Researched the optimization landscape of Gaussian Networks with Gradient Descent
%			\item Discovered a novel source of vanishing gradient impeding the training using backpropagation
%		\end{itemize}
%		\vspace{8pt}
%        
%        \textbf {Collaborative filtering for movie rating prediction}\\
%		Matrix completion using mixture of Gaussians \\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Designed questions and solutions with fellow TA He Sun and professor Tommi S Jaakola
%            \item Helped implement code that solved project with EM algorithm for matrix completion
%		\end{itemize}
%		\vspace{8pt}
%        
%        \textbf {Survey in Statistical Learning Theory}\\
%		Graduate project for class 9.520/6.860 2014\\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Prepared a survey on Uniform Stability and Generalization in Learning theory
%            \item Survey contained conceptual explanation to mathematical concepts in learning theory
%            \item Survey also contained my own presentation of the proof for the theorems
%			\item Survey can be read at: \href{https://www.quora.com/profile/Brando-Miranda/Posts/Uniform-Stability-and-Generalization-in-Learning-theory}{project report}
%		\end{itemize}
%		\vspace{8pt}
%        
%        \textbf {Survey in Theoretical Computer Science}\\
%        Project for graduate class in mathematics 18.409 2015\\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Research paper survey on provable algorithms that require less computation time given more training examples
%            \item In the case of SVM optimization PEGASOS requires less runtime assuming a target generalization
%            \item When learning halfspaces over sparse vectors, more training examples reduce the training runtime from exponential to polynomial time
%            \item Provided my unique outline of the main proof for halfspaces time reduction
%		\end{itemize}
%		\vspace{8pt}
%        
%        \textbf {Evaluating sublinear estimators for big data}\\
%        undergraduate thesis project, advised by professor Samuel Madden \\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Designed sub-linear sampling algorithms for estimating groups from big data in databases
%            \item Designed and proved that the algorithmic estimators were statistically consistency and unbiased
%            \item Experimentally evaluated the algorithms with synthetic data sets using the Mean Absolute Percentage Error
%		\end{itemize}
%		\vspace{8pt}
%	
%		\textbf {Road Runner}\\
%		Persistent, fault-tolerant, high-performance KV store \\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Built Multipaxos library for efficient consensus
%			\item Optimized disk I/O with batching scheme
%			\item Tested with mocks simulating RPC delays on unreliable, long-distance network
%		\end{itemize}
%		\vspace{8pt}
%	
%		\textbf {Dark Cloud}\\
%		Secure, shared, cloud filesystem on untrusted server \\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Designed layered cryptography scheme
%			\item Implemented the cryptography API
%            \item Report: \href{https://css.csail.mit.edu/6.858/2013/projects/mpolanco-pcattori-brando90.pdf}{project report}
%		\end{itemize}
%		\vspace{8pt}
%		
%		\textbf {BattleCode} \\
%		Artificial Intelligence competition\\
%		\vspace*{-3pt}
%		\begin{itemize} \itemsep -2pt
%			\item Wrote path finding algorithms \& distributed combat strategy
%			\item Finalists in competition pool of 300 teams
%			\item Awarded \emph{Best Strategy Report}
%		\end{itemize}
%	\end{multicols}
%\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certification

\header{Certification}
\begin{body}
	\vspace{12pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item Coursera: Learning how to Learn: Powerful mental tools to help you master tough subjects (with Honors), awarded by UC San Diego, Dr. Barbara Oakley, Dr. Terrence Sejnowski \& Linda Walker
	\end{itemize}
	\begin{itemize} \itemsep -2pt  % reduce space between items
		\item Coursera: Mindshift: Break Through Obstacles to Learning and Discover Your Hidden Potential (with Honors), by McMaster University Dr. Barbara Oakley, Dr. Terrence Sejnowski \& Linda Walker
	\end{itemize}
	\begin{itemize}
	    \item Certified Dance instructor with the World-Mastery program: completed the online training by world renowned artists Korke \& Judith
	\end{itemize}
% 	\begin{itemize} \itemsep -2pt  % reduce space between items
% 		\item Coursera: Creativity, Innovation, and Change, by Pennsylvania State University, Dr. Jablokow, Dr. Velegol, Dr. Matson et al. (under progress)
% 	\end{itemize}
%     \begin{itemize} \itemsep -2pt  % reduce space between items
%     \item Coursera: Synapses, Neurons and Brains, Hebrew University of Jerusalem, Dr. Idan Segev (under progress)
%     \end{itemize}
%     space{12pt}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\newpage
\header{Leadership}

\begin{body}
	\vspace{12pt}

	\textbf{Stanford AI for Lean (Lean AI Club)} - Stanford, CA \hfill \emph{2025 - Present}\\
	\emph{Founding Member} --- \href{https://www.stanfordlean.club/}{Stanford Lean AI Club} (also \href{https://aiforlean.org/}{aiforlean.org}), a research community advancing AI for Lean theorem proving and formalizing mathematics.\\
	\vspace{8pt}

	\textbf{Stanford Bachata Sensual \& Brazilian Zouk (\href{https://sbsbz-dance.manus.space/}{SBSBZ})} - Stanford, CA \hfill \emph{September 2021 - Present}\\
	\emph{Founder \& President} --- founded the first Bachata Sensual \& Zouk student organization at Stanford; 200+ members; open-access lesson summaries on YouTube.\\
	\vspace{8pt}

	\textbf{UIUC Latinos in Computer Science (LCS)} - Urbana-Champaign, IL \hfill \emph{December 2019 - Present}\\
	\emph{Graduate Advisor} --- founded the LCS Professional \& Wellness Development Colloquium speaker series.\\
	\vspace{8pt}

	\textbf{UIUC Bachata Sensual \& Zouk (Latin Dance Group)} - Urbana-Champaign, IL \hfill \emph{January 2019 - December 2021}\\
	\emph{Founder \& President} --- founded the first Bachata Sensual \& Zouk group at UIUC. \textbf{Bachata Sensual Excellence Diploma}, Korke \& Judith \textit{World Mastery} (Beginner, Intermediate, Advanced), 2019.\\

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Activities
\header{Activities}

\begin{body}
	\vspace{12pt}
    \textbf{MIT Chamber Music Society} - Cambridge, MA \hfill \emph{September 2011 - June 2014}\\
	\emph{Jazz Musician}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Alto Saxophone player with MIT's Jazz combo as part of the Chamber Music Society lead by Boston jazz artist 
		Keala Kaumeheiwa
        \item Performed, Composed and arranged several Jazz pieces
	\end{itemize}
	\vspace{8pt}
    
    \textbf{MIT Wind Ensemble (MITWE)} - Cambridge, MA \hfill \emph{February 2011 - June 2011}\\
	\emph{Clarinetist}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt  % reduce space between items
    	\item Clarinet player with director Dr. Harris
        \item Performed with the Wind Ensemble at the MIT 150th Convocation 
	\end{itemize}
	\vspace{8pt}
    
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Websites

% \header{Websites}
% \begin{body}
% 	\vspace{12pt}
% 	https://brando90.github.io/brandomiranda/
	
% 	https://cbmm.mit.edu/about/people/miranda

% 	https://www.linkedin.com/in/brando-miranda-40821046/
    
%     https://github.com/brando90
    
%     https://stackexchange.com/users/1589784/charlie-parker?tab=accounts
    
%     https://www.quora.com/profile/Brando-Miranda
    
% \end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Group Identity
\header{Family Background}

\begin{body}
	\vspace{12pt}
Latino/Hispanic, Mexican heritage.
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
%\header{Awards and Honors}

\end{document}
