\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{lipsum}
\usepackage{multicol}
\usepackage[hidelinks,pageanchor=false]{hyperref}
%\usepackage{href}


\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

%\usepackage[margin=0.0in]{geometry}
\usepackage{geometry}
 \geometry{
% a4paper,
 textwidth=170mm,
 left=1in,
 top=20mm,
 bottom=18mm,
 }

% \leftmargin=0.25in
% \oddsidemargin=0.25in
% \textwidth=6.0in
% \topmargin=-0.25in
% \textheight=9.25in

\raggedright

% Even bottom margin across pages: stretch inter-paragraph glue
% rather than letting pages end short (default \raggedbottom).
% Publication entries use \\* (not \\) between title/authors/venue so
% LaTeX cannot insert a page break inside an entry — see CV margin rule.
\flushbottom
\widowpenalty=10000     % no widow lines (first line of paragraph at page bottom)
\clubpenalty=10000      % no orphan lines (last line of paragraph at page top)
\setlength{\parskip}{0pt plus 18pt}   % stretchable glue for \flushbottom to consume
\setlength{\parskip}{0pt plus 6pt}

\pagenumbering{gobble}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
	\nopagebreak[4]    % keep section content with its header (prevent orphan headers)
}

\newenvironment{body} {
		\vspace*{-16pt}
		\begin{changemargin}{-0.25in}{-0.5in}
	  }
		{\end{changemargin}\vspace{8pt plus 12pt}
	}

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

\newcommand{\tab}{\hspace*{2em}}

\newcommand{\bul}{$\bullet$ \hspace*{0em}}

\newcounter{pubnum}
\newcommand{\pubitem}{\stepcounter{pubnum}(\thepubnum)~}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{changemargin}{-0.5in}{-0.5in}
\noindent\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l c r}
\begin{tabular}[c]{@{}l@{}}\small\textbf{brando9@stanford.edu}\\\small Stanford, CA 94305\end{tabular}
&
{\Huge \bfseries Brando Miranda}
&
\begin{tabular}[c]{@{}r@{}}\small Gates Bldg., 353 Jane Stanford Way\end{tabular}
\end{tabular*}
\par\vspace{4pt}
\begin{center}
\href{https://scholar.google.com/citations?user=_NQJoBkAAAAJ&hl=en}{Google Scholar} $\mid$
\href{https://brando90.github.io/brandomiranda/}{Website} $\mid$
\href{https://x.com/BrandoHablando}{X (formerly Twitter)} $\mid$
\href{https://www.linkedin.com/in/brando-miranda-40821046/}{LinkedIn} $\mid$
\href{https://profiles.stanford.edu/brando-miranda}{Stanford Profile} $\mid$
\href{https://cbmm.mit.edu/about/people/miranda}{MIT CBMM Profile}
\end{center}
\vspace{8pt}
\end{changemargin}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interests
\header{Research Interests}

\begin{body}
	\vspace{12pt}
	AI for formal mathematics --- Lean 4 theorem proving, autoformalization, and end-to-end formal verification of software and mathematics; contamination-resistant evaluation of LLM mathematical reasoning; data-centric machine learning for foundation and frontier models; alternative architectures (e.g.\ energy-based models) toward Artificial General Intelligence (AGI).
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{12pt}
	\textbf{Ph.D. in Computer Science} \hfill \emph{2022-2026 (expected)}\\
	\emph{Stanford University} \hfill \text{GPA: 4.045/4.0}\\
	\textbf{Advisor: Prof. Sanmi Koyejo, Stanford Trustworthy AI Research Group (STAIR).}\\

	\smallskip
	\textbf{Master of Engineering in Electrical Engineering and Computer Science} \hfill \emph{2014-2016}\\
	\emph{Massachusetts Institute of Technology} \hfill \text{GPA: 4.8/5.0}\\
	\textbf{Advisor: Prof. Tomaso Poggio, Center for Brains, Minds and Machines.}\\
	Thesis Title: \emph{Function Approximation with Deep Neural and Gaussian Networks}.\\

	\smallskip
	\textbf{Bachelor of Science, Computer Science and Engineering} \hfill \emph{2010-2014}\\
	\emph{Massachusetts Institute of Technology} \hfill \text{Minors: Mathematics, Music}\\
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards & Honors
\header{Awards \& Honors}
\begin{body}
\vspace{12pt}
\begin{itemize} \itemsep -2pt
    \item \textbf{ICML 2026 Silver Reviewer} (May 2026) --- top reviewer recognition, signed by the ICML 2026 Program Chairs.
    \item \textbf{Oral Recommendation (Top 1)}, 2nd AI for Math Workshop @ ICML 2025 --- for \textit{VeriBench: End-to-End Formal Verification Benchmark for AI Code Generation in Lean 4} (Miranda et al.); reviewer recommendation ``Accept (Oral, Top 1)''.
    \item \textbf{Pear AI Researchers Circle} (July 2025) --- selective AI-researcher network convened by Pear VC; invited following the final round (R3) of the Pear AI Researcher Grant program.
    \item \textbf{ICML Workshop on Trustworthy Multi-modal Foundation Models and AI Agents (TiFA) --- Outstanding Paper Award} (July 2024) --- for ``Why Has Predicting Downstream Capabilities of Frontier AI Models with Scale Remained Elusive?'' (Schaeffer, Schoelkopf, Miranda, et al.).
    \item \textbf{NeurIPS Outstanding Main Track Paper Award} (December 2023) --- top 0.4\% of NeurIPS submissions; only 2 main-track papers selected. For ``Are Emergent Abilities of Large Language Models a Mirage?'' (Schaeffer, Miranda, Koyejo).
    \item \textbf{EDGE Scholar}, Stanford University (September 2022) --- Stanford fellowship supporting first-generation / low-income PhD scholars.
    \item \textbf{Stanford School of Engineering Fellowship} (September 2022) --- multi-year departmental fellowship for incoming engineering PhDs.
    \item \textbf{Honorable Mention}, Ford Foundation Predoctoral Fellowship (2020, 2021) --- national fellowship recognizing PhD applicants with potential to diversify the U.S. professoriate.
    \item \textbf{Best Research Project Award}, UIUC graduate course CS 598 ``Learning to Learn'' (December 2020) --- course-level award for the top research project.
    \item \textbf{HSF Scholar}, Hispanic Scholarship Fund (2020) --- competitive national merit fellowship for Hispanic graduate students.
    \item \textbf{Computer Science Excellence Saburo Muroga Endowed Fellow}, UIUC (2019-2020) --- top departmental fellowship for incoming CS PhDs.
    \item \textbf{Most Cited Paper Certificate}, International Journal of Automation \& Computing (IJAC, December 2019) --- for ``Why and when can deep- but not shallow-networks avoid the curse of dimensionality: a review''.
	\item \textbf{Sloan Scholar}, Alfred P. Sloan Foundation Minority Ph.D. (MPHD) Program (2018-2019) --- national fellowship for underrepresented STEM PhD students.
	\item \textbf{Grainger Engineering SURGE Fellowship}, UIUC (2018-2019) --- multi-year college-level fellowship for diverse engineering PhDs.
\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Selected Publications
\newpage
\header{Selected Publications}
\begin{body}
    \small
    \vspace{8pt} % DONT REMOVE THIS

    \vspace{4pt}
    \emph{\href{https://scholar.google.com/citations?user=_NQJoBkAAAAJ&hl=en}{Google Scholar}: full publication list.}

    \vspace{8pt}
    \textbf{Refereed Publications}
    \par\nopagebreak[4]\vspace{4pt}
    \setcounter{pubnum}{0}

    \pubitem \href{https://openreview.net/forum?id=vdXPorr099}
    {E. Chen, A. Gulati, \textbf{B. Miranda}, Z. Tang, S. Koyejo,
    \emph{Rethinking LLM Judges: Chain-of-Thought and Multi-Step Pipelines for Math Grading}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Workshop on Logical Reasoning of Large Language Models. 2026})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=8OoZ8dnvIT}
    {Z. Zhou, X. Lu, C. Cao, \textbf{B. Miranda}, T. Liu, B. Han, S. Koyejo,
    \emph{CoDaPO: Confidence and Difficulty-Adaptive Policy Optimization for LLM Reasoning}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Workshop on Lifelong Agents: Learning, Aligning, Evolving. 2026} \& \textbf{2nd Workshop on AI for Math at International Conference on Machine Learning (ICML). 2025})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=wDjOpXKgtU}
    {S. Barkallah, S. Daruru, \textbf{B. Miranda}, L. Aniva, A. Nie, S. Koyejo,
    \emph{VeriBench-FTP: A Formal Theorem Proving Benchmark in Lean 4 for Code Verification}.}
    \\*
    (\textbf{5th Neural Information Processing Systems (NeurIPS) Workshop on Mathematical Reasoning and AI. 2025})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=rWkGFmnSNl}
    {\textbf{B. Miranda}, Z. Zhou, A. Nie, E. Obbad, L. Aniva, K. Fronsdal, W. Kirk, D. Soylu, et al.,
    \emph{VeriBench: End-to-End Formal Verification Benchmark for AI Code Generation in Lean 4}.}
    \\*
    (\textbf{2nd Workshop on AI for Math at International Conference on Machine Learning (ICML). 2025})

    \vspace{10pt}
    \pubitem \href{https://link.springer.com/chapter/10.1007/978-3-031-90643-5_6}
    {L. Aniva, C. Sun, \textbf{B. Miranda}, C. Barrett, S. Koyejo,
    \emph{Pantograph: A machine-to-machine interaction interface for advanced theorem proving, high level reasoning, and data extraction in Lean 4}.}
    \\*
    (\textbf{International Conference on Tools and Algorithms for the Construction and Analysis of Systems (TACAS). 2025})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2508.08292}
    {A. Gulati, \textbf{B. Miranda}, E. Chen, E. Xia, K. Fronsdal, B. de Moraes Dumont, S. Koyejo,
    \emph{Putnam-AXIOM: A Functional \& Static Benchmark for Measuring Higher Level Mathematical Reasoning in LLMs}.}
    \\*
    (\textbf{International Conference on Machine Learning (ICML). 2025} \& \textbf{Neural Information Processing Systems (NeurIPS) Workshop on Mathematics and AI (MATH-AI). 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/pdf/2406.04391}
    {R. Schaeffer, H. Schoelkopf, \textbf{B. Miranda}, G. Mukobi, V. Madan, A. Ibrahim, H. Bradley, S. Biderman, S. Koyejo,
    \emph{Why Has Predicting Downstream Capabilities of Frontier AI Models with Scale Remained Elusive?}.}
    \\*
    (\textbf{International Conference on Machine Learning (ICML). 2025} \& \textbf{International Conference on Machine Learning (ICML) Workshop on Trustworthy Multi-modal Foundation Models and AI Agents (TiFA). 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2601.04301}
    {R. Schaeffer, J. Kazdan, B. Abbasi, K. Z. Liu, \textbf{B. Miranda}, A. M. Ahmed, F. Berez, et al.,
    \emph{Quantifying the Effect of Test Set Contamination on Generative Evaluations}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS) Workshop on Evaluating the Evolving LLM Lifecycle. 2025})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2506.19882}
    {R. Schaeffer, J. Kazdan, Y. Denisov-Blanch, \textbf{B. Miranda}, M. Gerstgrasser, et al.,
    \emph{Position: Machine Learning Conferences Should Establish a `Refutations and Critiques' Track}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS), Main Track. 2025})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=wvFnqVVUhN}
    {R. Schaeffer, D. Valentine, L. Bailey, J. Chua, et al., \textbf{B. Miranda}, et al., S. Koyejo, E. Perez,
    \emph{Failures to Find Transferable Image Jailbreaks Between Vision-Language Models}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR). 2024} \& \textbf{Neural Information Processing Systems (NeurIPS) Workshop on Red Teaming Generative AI. 2024})

    \vspace{10pt}
    \pubitem \href{https://openreview.net/forum?id=f6IB0WrOKS}
    {R. Schaeffer, M. Khona, S. Chandra, M. Ostrow, \textbf{B. Miranda}, S. Koyejo,
    \emph{Does Maximizing Neural Regression Scores Teach Us About The Brain?}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS) Workshop on Unifying Representations in Neural Models (UniReps), 2nd Edition. 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2501.08496}
    {K. Chawla, A. Sahai, M. DePavia, S. Sundar, \textbf{B. Miranda},
    \emph{Quantifying the Importance of Data Alignment in Downstream Model Performance}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Workshop on Data-Centric Machine Learning Research (DMLR). 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2406.06555}
    {A. Gulati, D. Ladsaria, S. Mishra, J. Sidhu, \textbf{B. Miranda},
    \emph{An Evaluation Benchmark for Autoformalization in Lean4}.}
    \\*
    (\textbf{International Conference on Learning Representations (ICLR) Tiny Papers Track, Second Edition. 2024})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2304.15004}
    {R. Schaeffer, \textbf{B. Miranda}, S. Koyejo,
    \emph{Are Emergent Abilities of Large Language Models a Mirage?}.}
    \\*
    (\textbf{Neural Information Processing Systems (NeurIPS), Main Track. 2023})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2306.13840}
    {\textbf{B. Miranda}*, A. Lee*, P. Yu, S. Koyejo,
    \emph{Beyond Scale: the Diversity Coefficient as a Data Quality Metric Demonstrates LLMs are Pre-trained on Formally Diverse Data}.}
    \\*
    (\textbf{International Conference on Machine Learning (ICML) Workshop on Data-Centric Machine Learning. 2023} \& \textbf{International Conference on Machine Learning (ICML) Workshop on Deployable Generative AI. 2023}) (*equal contribution)

    \vspace{10pt}
    \pubitem \href{https://link.springer.com/article/10.1007/s11633-017-1054-2}
    {T. Poggio, H. Mhaskar, L. Rosasco, \textbf{B. Miranda}, Q. Liao,
    \emph{Why and when can deep-but not shallow-networks avoid the curse of dimensionality: a review}.}
    \\*
    (\textbf{International Journal of Automation and Computing (IJAC). 2017})

    \vspace{12pt}
    \textbf{Preprints and Technical Reports}
    \par\nopagebreak[4]\vspace{4pt}
    \setcounter{pubnum}{0}

    \pubitem \href{https://cs.stanford.edu/~daneshva/publications/ai-coding-benchmarks-need-proofs-not-just-tests.pdf}
    {D. Amrollahi, M. Karimi, \textbf{B. Miranda}, L. Aniva, C. Sun, C. Barrett, S. Koyejo,
    \emph{AI Coding Benchmarks Need Proofs, Not Just Tests}.}
    \\*
    (\textbf{Preprint 2026})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2502.15795}
    {W. Chan, M. Souliman, J. Nordhagen, \textbf{B. Miranda}, E. Obbad, S. Koyejo,
    \emph{Lean-ing on Quality: How High-Quality Data Beats Diverse Multilingual Data in Autoformalization}.}
    \\*
    (\textbf{Preprint 2025, arXiv:2502.15795})

    \vspace{10pt}
    \pubitem \href{https://arxiv.org/abs/2410.18194}
    {E. Obbad, I. Mlauzi, \textbf{B. Miranda}, R. Schaeffer, K. Obbad, S. Bedi, S. Koyejo,
    \emph{ZIP-FIT: Embedding-Free Data Selection via Compression-Based Alignment}.}
    \\*
    (\textbf{Preprint 2024, arXiv:2410.18194})
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Artifacts & Systems
\header{Research Artifacts \& Systems}

\begin{body}
	\vspace{12pt}
	\begin{itemize} \itemsep -2pt
		\item \textbf{\href{https://openreview.net/forum?id=rWkGFmnSNl}{VeriBench}} and \textbf{\href{https://openreview.net/forum?id=wDjOpXKgtU}{VeriBench-FTP}}: Lean 4 verification benchmarks for AI-generated code and theorem-proving code verification
		\item \textbf{\href{https://icml.cc/virtual/2025/poster/44232}{Putnam-AXIOM}} and \textbf{\href{https://huggingface.co/datasets/3ricme/Putnam-AXIOM-Grading}{Putnam-AXIOM-Grading}}: LLM mathematical reasoning benchmark and human-graded Putnam-style partial-credit benchmark
		\item \textbf{\href{https://link.springer.com/chapter/10.1007/978-3-031-90643-5_6}{Pantograph}}: Lean machine-to-machine theorem-proving interface
		\item \textbf{\href{https://huggingface.co/morph-labs/morph-prover-v0-7b}{Morph Prover v0 7b} / \href{https://www.moogle.ai/}{Moogle.ai}}: Lean 4 proof model and verified-code search engine developed with Morph Labs
		\item \textbf{\href{https://alphaapollo.org/}{AlphaApollo}} and \textbf{\href{https://github.com/dhoemenk97-star/AlphaDiana}{AlphaDiana}}: agentic reasoning and harness-aware evaluation systems for verifiable reasoning
		\item \textbf{\href{https://github.com/brando90/ultimate-utils}{ultimate-utils}}: reusable ML and research-engineering utility library
	\end{itemize}
\end{body}

% Professional Experience
\header{Professional Experience}

\begin{body}
	\vspace{12pt}

    \textbf{Stanford University} - Stanford, CA \hfill \emph{September 2022 - 2026 (expected)}\\*
	\emph{Ph.D. Student in Computer Science. Advisor: Professor Sanmi Koyejo}\\*
	Research in AI for formal mathematics; mentored a \href{https://www.cs.stanford.edu/bachelors/research-opportunities}{Stanford CS CURIS} intern and student collaborators on Lean 4 verification research.\\
	\vspace{8pt}

    \textbf{Amazon Web Services (AWS)} - Cupertino, CA \hfill \emph{June 2024 - September 2024}\\*
	\emph{Applied Scientist Intern}\\
	\vspace{8pt}

    \textbf{Morph Labs} - Remote \hfill \emph{October 2023 - December 2023}\\*
	\emph{Machine Learning Research Scientist Consultant}\\
	\vspace{8pt}

	\textbf{Wise Agents} - Stanford Spin-out \hfill \emph{2023}\\*
	\emph{AI Research Consultant}\\
	\vspace{8pt}

	\textbf{IBM Research} - Yorktown Heights, NY \hfill \emph{May 2022 - August 2022}\\*
	\emph{Graduate Research Intern}\\
	\vspace{8pt}

	\textbf{University of Illinois Urbana-Champaign} - Urbana-Champaign, IL \hfill \emph{September 2018 - May 2022}\\*
	\emph{Ph.D. Student in Computer Science. Advisor: Professor Sanmi Koyejo}\\*
	Research on meta-learning and data diversity; mentored student collaborators on data quality and evaluation methodology.\\
	\vspace{8pt}

	\textbf{IBM Research} - Yorktown Heights, NY \hfill \emph{May 2021 - August 2021}\\*
	\emph{Graduate Research Intern}\\
	\vspace{8pt}

	\textbf{MIT CBMM (Center for Brain Minds \& Machines)} - Cambridge, MA \hfill \emph{June 2015 - September 2018}\\*
	\emph{Research Assistant. Advisor: Professor Tomaso Poggio}\\*
	Deep-learning theory research; mentored undergraduate collaborators through MIT CBMM's Engineering of Intelligence team.\\

\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Media Coverage

\header{Media Coverage}
\begin{body}
\vspace{12pt}
\begin{itemize} \itemsep -2pt
    \item \textbf{Hacker News / Y Combinator (January 2025)}: \href{https://news.ycombinator.com/item?id=42565606}{\textit{Putnam-AXIOM} benchmark posted on Hacker News} --- front-page attention on Y Combinator's tech-news forum
    \item \textbf{Aran Komatsuzaki / @arankomatsuzaki on X (June 2024)}: \href{https://x.com/arankomatsuzaki/status/1799976398331011173}{shared the downstream-capabilities paper on X} to his AI-research audience
    \item \textbf{AIhub (April 2024)}: \href{https://aihub.org/2024/04/25/are-emergent-abilities-of-large-language-models-a-mirage-interview-with-brando-miranda/}{interview with Brando Miranda} on the NeurIPS Outstanding Paper Award-winning emergent-abilities paper
    \item \textbf{American Scientist (March-April 2024)}: \href{https://www.americanscientist.org/article/an-education-in-irrationality}{``Is There an AI Metrics Mirage?''}
    \item \textbf{White House Economic Report of the President (March 2024)}: cited Miranda et al.'s work on emergent abilities in the White House's annual economic-policy report
    \item \textbf{Andrew Ng (March 2024)}: Endorsed the emergent-abilities paper as evidence for smooth, predictable AGI development
    \item \textbf{Quanta Magazine (February 2024)}: ``How Quickly Do Large Language Models Learn Unexpected Skills?''
    \item \textbf{Stanford AI Lab Blog (ICML 2023)}: \href{https://ai.stanford.edu/blog/icml-2023/}{featured the \textit{Beyond Scale} and \textit{Is Pre-training Truly Better Than Meta-Learning?} papers}
    \item \textbf{AK / @\_akhaliq on X (June 2023)}: \href{https://x.com/_akhaliq/status/1673507375515594766}{shared the \textit{Beyond Scale} paper on X} to a large AI-research audience (68.9K views)
    \item \textbf{The New York Times (June 2023)}: ``Silicon Valley Confronts the Idea That the `Singularity' Is Here''
    \item \textbf{The Register (May 2023)}: \href{https://www.theregister.com/software/2023/05/16/llm-emergent-behavior-written-off-as-a-mirage-by-study/655184}{``LLM emergent behavior written off as `a mirage' by study''}
    \item \textbf{Stanford Institute for Human-Centered Artificial Intelligence (HAI) (May 2023)}: \href{https://hai.stanford.edu/news/ais-ostensible-emergent-abilities-are-mirage}{``AI's Ostensible Emergent Abilities Are a Mirage''}
    \item \textbf{Y Combinator News (May 2023)}: \href{https://news.ycombinator.com/item?id=35768824}{``Are emergent abilities of large language models a mirage?''}
    \item \textbf{Forbes (May 2023)}: ``AI `Emergent Abilities' Are A Mirage, Says AI Researcher''
    \item \textbf{Vice / Motherboard (May 2023)}: \href{https://www.vice.com/en/article/scary-emergent-ai-abilities-are-just-a-mirage-produced-by-researchers-stanford-study-says/}{``Scary `Emergent' AI Abilities Are Just a `Mirage' Produced by Researchers, Stanford Study Says''}
    \item \textbf{Additional coverage}: Medium, Hacker News, NeurIPS blog, Reddit, and other community discussions
\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Invited & Contributed Talks

\header{Invited \& Contributed Talks}
\begin{body}
\vspace{12pt}
\begin{itemize} \itemsep -2pt
    \item \textbf{Applications of Trustworthy Machine Reasoning with AI Coding Agents} -- \href{https://trustworthy-machine-reasoning.github.io/}{AAAI 2026 Tutorial} ``Trustworthy Machine Reasoning with Foundation Models'' (Part IV, 50 min), Singapore, January 2026
    \item \textbf{Emergent Abilities in Large Language Models: Mirage or an Elusive Predictive Frontier?} -- \href{https://docs.google.com/presentation/d/1J29Rt6C7g8uh6aWUJUIUtuZHdU0ihrWMi8C66XJn9jw/edit?usp=sharing}{Hong Kong Baptist University, Department of Computer Science Seminar}, Hong Kong, January 2026
    \item \textbf{Applications of Trustworthy Machine Reasoning with AI Coding Agents} -- \href{https://docs.google.com/presentation/d/1oHnxUTewe0k9h-SL8RExViJVOUcEPnWmPD_VbD4EzJ0/edit?usp=sharing}{Hong Kong Baptist University, Department of Computer Science Seminar}, invited, January 2026
    \item \textbf{VeriBench: End-to-End Formal Verification Benchmark for AI Code Generation in Lean 4} -- Lawrence Livermore National Laboratory Reading Group, invited, July 2025
    \item \textbf{Intro to Lean 4, VeriBench, and Trustworthy Testing with Theorems} -- \href{https://docs.google.com/presentation/d/1KRBym-sOORaxszOJQHdD4u80wAl7jHy8Pda0KAcdeZw/edit?usp=sharing}{Prof. Azalia Mirhoseini's Lab Meeting, Stanford}, invited, 2025
    \item \textbf{Are Emergent Abilities of Large Language Models a Mirage?} -- \href{https://docs.google.com/presentation/d/1k-yCVLob1eSyg71jT-k2w2mi--gkTQGAK_H2x3sPqpA/edit?usp=sharing}{Stanford IEEE Invited Talk}, Stanford, CA, 2023
    \item \textbf{The Curse of Low Task Diversity: On the Failure of Transfer Learning to Outperform MAML} -- \href{https://neurips.cc/virtual/2022/63778}{NeurIPS Meta-Learning Workshop, Contributed Talk}; \href{https://docs.google.com/presentation/d/1nY39x8u8j7k6KpOhD6Vqto78YzLOwyR9B24kuoHJijY/edit?usp=sharing}{slides}, New Orleans, LA, December 2022
\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching

\header{Teaching Experience}
\begin{body}
	\vspace{12pt}

    \textbf{Stanford University} \hfill \emph{2023 - 2024}\\
	\emph{Course Assistant (3 quarters) \& Instructor of Record (Spring)}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item CS 197 \textit{How to Do CS Research} with Prof. Michael Bernstein --- TA'd 3 quarters; \textbf{Instructor of Record} for the Spring offering
		\item Mentored undergraduate research that produced \textbf{2 workshop publications} (including ICML workshop tracks)
	\end{itemize}

    \textbf{University of Illinois Urbana-Champaign} \hfill \emph{August 2020 - December 2020}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
		\item CS 446 Machine Learning
		\item Designed problem sets and exams; held weekly office hours
	\end{itemize}
    
    \textbf{Massachusetts Institute of Technology} \hfill \emph{2014-2016}\\
	\emph{Graduate Teaching Assistant}\\
	\vspace*{-3pt}
	\begin{itemize} \itemsep -2pt
	\item Statistical Learning Theory \& Applications (9.520/6.860); Introduction to Machine Learning (6.036)
        \item Introduction to Algorithms (6.006); Design \& Analysis of Algorithms (6.046)
	\end{itemize}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Leadership
\header{Leadership \& Service}

\begin{body}
    \vspace{12pt}

\textbf{Research Mentorship} \hfill \emph{2016 - Present}\\
\vspace*{-3pt}
\begin{itemize} \itemsep -2pt
    \item Mentored undergraduate and graduate students at Stanford, UIUC, and MIT CBMM, including a \href{https://www.cs.stanford.edu/bachelors/research-opportunities}{Stanford CS CURIS} intern
    \item Led research teams on data quality metrics, meta-learning, and formal reasoning
\end{itemize}
\vspace{8pt}

\textbf{Academic Service} \hfill \emph{2018 - Present}\\
\vspace*{-3pt}
\begin{itemize} \itemsep -2pt
    \item Co-founder and president of \href{https://www.stanfordlean.club/}{Stanford AI for Lean}; created public \href{https://www.youtube.com/playlist?list=PLB3sDpSRdrOt68MTR6kdI0Jc85Uuw1YWV}{Learning Lean 4 tutorial videos} with a companion \href{https://github.com/brando90/learning_lean/tree/main}{code repository}
    \item Reviewer for NeurIPS 2026, ICLR 2026, ICML 2026 (\textbf{Silver Reviewer} -- top reviewer recognition), ICLR 2025, ICML 2025 AI4MATH Workshop, ICLR 2024 DMLR Workshop, NeurIPS 2023 MATH-AI Workshop, ICLR 2020, JMLR 2018
    \item Graduate advisor for Latinos in Computer Science (LCS) at UIUC
    \item Founded "Stanford Bachata Sensual \& Brazilian Zouk" and "UIUC Bachata Sensual \& Zouk" official student organizations; Stanford group has an \href{https://www.youtube.com/playlist?list=PLB3sDpSRdrOt6iKyPucMJAwbwW2YtMs3V}{83-video YouTube lesson playlist} with 25K+ total video views and \href{https://www.instagram.com/stanford_bachata_sensual_zouk/}{Instagram}
    \item Undergraduate and outreach research mentorship through \href{https://www.cs.stanford.edu/bachelors/research-opportunities}{Stanford CS CURIS} (Summer 2025), DREU at UIUC, UROP at MIT, and MIT CBMM's Engineering of Intelligence Team
\end{itemize}

\end{body}

\end{document}
